---
title: "Bangladesh CCDR - 01. Chapter 1"
date: "03/11/2022"
output:
  github_document: default
  html_document: default
knit: (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_format = "github_document");
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_format = "html_document",
                        output_dir=file.path(dirname(inputFile), "../html/"))                  
      })
---

Chapter 1 description

```{r, echo=FALSE, results='hide', message=FALSE}
source("../../styles/SAR_CCDR_style.R")
source("../../utils/CCDR_utils.R")
library(knitr)
library(dplyr)
library(tidyr)
library(tidyverse)
library(stringr)
library(ggplot2)
library(ggalt)
library(forcats)
library(png)
library(ggpubr)
library(ggrepel)
library(scales)
library(hrbrthemes)
library(viridis)
library(wbstats)
library(wbgcharts)
library(wbgmaps)
library(wbggeo)
library(readr)
library(readxl)
library(gtable)
library(grid)
library(lubridate)
library(extrafont)
# this only needs to be done once
# library(remotes)
# remotes::install_version("Rttf2pt1", version = "1.3.8")
# font_import() 
# loadfonts(device = 'win')
create_wbgref()
```





&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Economic growth

Data source: WDI

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=3.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_economic_growth <- function() {

  # data
  df <- wb_data(
    indicator = c("NY.GDP.PCAP.PP.CD"),
    country = c("BGD", "LMC", "SAS"),
    start_date = 1990,
    end_date = 2020
  )
  df <- df %>% 
    mutate(num_def = NY.GDP.PCAP.PP.CD) %>% 
    select(iso3c, country, date, num_def) 
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = date, y = num_def, group = rev(iso3c), color = iso3c)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$date), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df %>% filter(date == max(date)) %>% pull(num_def) %>% repel(gap=6),
            labels = df %>% filter(date == max(date)) %>% pull(country)
          )) +
        scale_color_manual(values = c(
          "XN" = style$colors$spot.secondary.light, 
          "SAS" = style$colors$spot.secondary.light,
          "BGD" = style$colors$spot.primary)) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Bangladesh's economic growth compared with South Asia and lower-middle-income group",
    subtitle = "GDP per capita, PPP (current international $), 1990 to 2020",
    source = "Source: World Development Indicators (NY.GDP.PCAP.PP.CD)."
  )
}

fig_ch1_economic_growth()

figure_save_draft_png(fig_ch1_economic_growth(), style_SAR_CCDR, "../png/fig_ch1_economic_growth.png", height=3.1, width=5.5)

```





&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Structure of economy

Data source: WDI

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=8.5, out.width=800, dpi=200}

fig_ch1_structure_of_economy <- function() {
  
# data
country_code = "BGD"
columns = c("iso2c", "iso3c", "country", "year", "Agriculture", "Industry", "Services")

indicators <- c("NV.AGR.TOTL.ZS", "NV.IND.TOTL.ZS", "NV.SRV.TOTL.ZS")
year <- 2020
df.nv <- wb_data(
  indicator = indicators,
  country = country_code,
  start_date = year,
  end_date = year
)

names(df.nv) = columns
for (x in colnames(df.nv)) attr(df.nv[[x]], "label") <- NULL
df.nv$indicator = "value added (% of GDP)"
 
indicators <- c("SL.AGR.EMPL.ZS", "SL.IND.EMPL.ZS", "SL.SRV.EMPL.ZS")
year <- 2019
df.empl <- wb_data(
  indicator = indicators,
  country = country_code,
  start_date = year,
  end_date = year
)

names(df.empl) = columns
for (x in colnames(df.empl)) attr(df.empl[[x]], "label") <- NULL
df.empl$indicator = "% of employment (modeled ILO estimate)"

indicators <- c("SL.AGR.EMPL.MA.ZS", "SL.IND.EMPL.MA.ZS", "SL.SRV.EMPL.MA.ZS")
year <- 2019
df.ma <- wb_data(
  indicator = indicators,
  country = country_code,
  start_date = year,
  end_date = year
)

names(df.ma) = columns
for (x in colnames(df.ma)) attr(df.ma[[x]], "label") <- NULL
df.ma$indicator = "% of male employment (modeled ILO estimate)"

indicators <- c("SL.AGR.EMPL.FE.ZS", "SL.IND.EMPL.FE.ZS", "SL.SRV.EMPL.FE.ZS")
year <- 2019
df.fe <- wb_data(
  indicator = indicators,
  country = country_code,
  start_date = year,
  end_date = year
)

names(df.fe) = columns
for (x in colnames(df.fe)) attr(df.fe[[x]], "label") <- NULL
df.fe$indicator = "% of female employment (modeled ILO estimate)"

df <- bind_rows(df.nv, df.empl, df.ma, df.fe) %>%
  gather(sector, value, c(Agriculture, Industry, Services)) %>%
  mutate(year = as.numeric(year))

# chart
indicator_labels = c("value added (% of GDP)", "% of employment (modeled ILO estimate)", "% of male employment (modeled ILO estimate)", "% of female employment (modeled ILO estimate)")
figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = "", y = value, fill = sector)) +
        geom_bar(width = 1, stat = "identity") +
        scale_fill_manual(values = c(
          Agriculture = style$colors$spot.secondary,
          Industry = style$colors$spot.primary.light,
          Services = style$colors$spot.primary
        )) +
        # geom_text(aes(y = ypos, label = sector), color = "white", size=2) +
        facet_grid(cols = vars(factor(indicator, levels=indicator_labels))) +
        # facet_grid(indicator ~ .) +
        # facet_grid(iso3c ~ ., labeller = as_labeller(str_wrap_lines(wbgref$regions$labels,3,force=TRUE))) + 
        coord_polar(theta = "y") +
        style$theme() +
        style$theme_legend("bottom") +
        theme(
          axis.text = element_blank(),
          panel.grid  = element_blank(),
          strip.text.x = element_text(angle = 0, hjust = 0.5),
          panel.spacing = unit(0, "npc")
        )
    },
    title = "Structure of ecomony in Bangladesh",
    subtitle = "Industry value added (2020) and employment breakdown (2019)",
    source = "Source: World Development Indicators"
  )
}

fig_ch1_structure_of_economy()

figure_save_draft_png(fig_ch1_structure_of_economy(), style_SAR_CCDR, "../png/fig_ch1_structure_of_economy.png", height=4.1, width=8.5)
```






&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Total energy supply (TES)

Data source: https://www.iea.org/data-and-statistics/data-browser/?country=BANGLADESH&fuel=Energy%20supply&indicator=TESbySource

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=6.5, out.width=800, dpi=200}

fig_ch1_TES_share_by_source <- function() {
  
  # data
  df <- read_csv("../data/Total energy supply (TES) by source - Bangladesh.csv", skip=4) %>%
    rename(year = X1) %>%
    select(-Units)
  df <- df %>%
    gather(source, TJ, 2:7) %>%
    group_by(year) %>%
    mutate(percentage =  100 *TJ/sum(TJ, na.rm=TRUE)) %>%
    mutate(year = as.numeric(year))
  
  # plot
  color_list <- c("#45462A", "#227C9D", "#BCAA99", "#3AAFB9", "#8E5572", "#BBBE64")
  figure(
    data = df,
    plot = function(data, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = year, y = percentage, fill = source)) +
        geom_area() +
        style$theme() + 
        style$theme_legend("right") +
        scale_x_continuous(expand = c(0, 1)) +
        # scale_y_continuous(labels = millions()) +
        scale_fill_manual(values=color_list)
      },
      aspect_ratio = 1.5,
      title = paste0("Bangladesh's total energy supply (TES)"),
      subtitle = "Share by source (%), 1990-2019",
      note = "Note: TES is made up of production + imports - exports - international marine bunkers - international aviation bunkers ± stock changes.",
      source = "Source: IEA World Energy Balances https://www.iea.org/data-and-statistics/data-product/world-energy-statistics-and-balances"
  )
}

fig_ch1_TES_share_by_source()

figure_save_draft_png(fig_ch1_TES_share_by_source(), style_SAR_CCDR, "../png/fig_ch1_TES_share_by_source.png", height=4.1, width=6.5)

```






&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Natural disasters

Data source: https://ourworldindata.org/natural-disasters
Country: Bangladesh
Disaster type: All disasters (by type)
Impact: Deaths, Economic damages (%GDP)
Timespan: Decadal average

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=5.5, out.width=800, dpi=200}
fig_ch1_natural_disasters <- function() {
  
  # data
  df1 <- read_csv("../data/natural-disasters_bangladesh_deaths.csv")
  names(df1) <- c('Entity', 'Code', 'Year', 'Extreme temperature', 'Wildfires', 'Storms', 
                  'Landslides', 'Mass movement (dry)', 'Volcanic activity', 'Earthquakes', 'Floods', 'Drought')
  df1 <- df1 %>%
    select(-c('Wildfires', 'Mass movement (dry)', 'Volcanic activity')) %>%
    gather(Type, Deaths, 4:9) %>%
    select(Year, Type, Deaths)
  
  df2 <- read_csv("../data/natural-disasters_bangladesh_gdp.csv")
  names(df2) <- c('Entity', 'Code', 'Year', 'Extreme temperature', 'Wildfires', 'Storms', 
                  'Landslides', 'Mass movement (dry)', 'Volcanic activity', 'Earthquakes', 'Floods', 'Drought')
  df2 <- df2 %>%
    select(-c('Wildfires', 'Mass movement (dry)', 'Volcanic activity')) %>%
    gather(Type, Damage, 4:9) %>%
    mutate(Damage = Damage*100) %>%
    select(Year, Type, Damage)
  
  df <- merge(df1, df2, by=c("Year", "Type"))
  
  # chart
  figure(
    data =  df,
    plot = function(df, style = style_SAR_CCDR()) {
      p <- ggplot(df, aes(x=Year, y=reorder(Type, desc(Type)), size=ifelse(Damage==0, NA, Damage), color=Deaths, fill=Deaths)) +
        geom_point(alpha=0.5, shape=21, color="black") +
        scale_size(range = c(1, 20), name="Damage (%GDP)",
                   breaks = c(10, 50,100),
                   labels = c("10", "50", "100")) +
        scale_fill_distiller(palette = "Spectral") + 
        scale_x_continuous(limits = c(1960, 2012), breaks = c(1960, 1970, 1980, 1990, 2000, 2010), labels = c("1960-1969", "1970-1979", "1980-1989", "1990-1999", "2000-2009", "2010-2019")) +
        xlab("Year") +
        ylab("Natural Disasters") +
        geom_curve(aes(x = 1975, y = 1.7, xend = 1970, yend = 1.3), 
                               colour = "#555555", 
                               size=0.3, 
                               curvature = 0.2,
                               arrow = arrow(length = unit(0.03, "npc"))) +
        annotate("text", x = 1975, y = 1.9, label = "including 1970 Bhola cyclone", size = 2.5, family = style$family) +
        style$theme() +
        theme(
          axis.title.x = element_text(vjust = -5),
          axis.title.y = element_text(angle = 90, vjust = 0, margin = margin(r = 15)),
          axis.text.x = element_text(angle = 0, vjust = 2), 
          legend.title = element_text(),
          legend.box.just = "center",
          legend.position = "right"
        )
    },
    aspect_ratio = 1,
    title = "Floods and storms are the most damaging natural disasters in Bangladesh",
    subtitle = "Decadal average: Number of deaths and economic damages (% GDP) from natural disasters",
    note = "Note: Decadal figures are measured as the annual average over the subsequent ten-year period.",
    source = "Source: Our World in Data."
  )
}

fig_ch1_natural_disasters()

figure_save_draft_png(fig_ch1_natural_disasters(), style_SAR_CCDR, "../png/fig_ch1_natural_disasters.png", height=4.1, width=5.5)
```




&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## National GHG Emission Profile 

Data source: https://www.climatewatchdata.org/data-explorer/historical-emissions?historical-emissions-data-sources=cait&historical-emissions-gases=all-ghg&historical-emissions-regions=All%20Selected%2CBGD&historical-emissions-sectors=All%20Selected&page=1
Source: CAIT
Country: Bangladesh
Sector: All selected
Gases: All GHG

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=5.1, fig.width=5.5, out.width=800, dpi=200}
fig_ch1_greenhouse_gas_emissions <- function() {
  
  # data
  df <- read_csv("../data/historical_emissions.csv")
  df <- df[-c(1,2),] %>%
    gather(key="Year", value="Emissions", "2018":"1990") %>%
    select(Sector, Year, Emissions) %>%
    mutate(Year = as.numeric(Year))
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = Year, y = Emissions, group = Sector, color = Sector)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$Year), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df %>% filter(Year == max(Year)) %>% pull(Emissions) %>% repel(gap=6),
            labels = df %>% filter(Year == max(Year)) %>% pull(Sector)
          )) +
        scale_color_manual(values = c(
          "Agriculture" = "#A43031", 
          "Building" = "#888D8E",   
          "Bunker Fuels" = "#888D8E",   
          "Electricity/Heat" = "#CB6655",   
          "Energy" = "#A41623",   
          "Fugitive Emissions" = "#888D8E",  
          "Industrial Processes" = "#888D8E",
          "Land-Use Change and Forestry" = "#888D8E",
          "Manufacturing/Construction" = "#888D8E",
          "Other Fuel Combustion" = "#888D8E",
          "Transportation" = "#888D8E",
          "Waste" = "#888D8E"),
          labels = unique(df$Sector)) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Energy and agriculture sectors take up the largest portions of greenhouse gas emissions in Bangladesh",
    subtitle = "Historical Country Greenhouse Gas Emissions (MtCO2e), 1990-2018",
    source = "Source: Climate Watch Historical Country Greenhouse Gas Emissions Data (1990-2018)."
  )
}

fig_ch1_greenhouse_gas_emissions()

figure_save_draft_png(fig_ch1_greenhouse_gas_emissions(), style_SAR_CCDR, "../png/fig_ch1_greenhouse_gas_emissions.png", height=5.1, width=5.5)
```





&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Vulnerability score

Data source: https://gain.nd.edu/our-work/country-index/download-data/

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=4.1, out.width=800, dpi=200}
library(ggradar)
library(showtext)

fig_ch1_vulnerability <- function() {
  
  # data
  df <- read_csv("../data/vulnerability.csv")

  # add regions and income levels
  df <- df %>%
    rename(iso3c = ISO3) %>%
    left_join(wbgref$countries$regions, by="iso3c") %>%
    left_join(wbgref$countries$incomegroups, by="iso3c")
  
  # calculate aggregates by regions
  region_aggregates <- df %>%
    group_by(region_iso3c) %>% summarize(ecosystems = mean(ecosystems, na.rm=TRUE),
                                         food = mean(food, na.rm=TRUE),
                                         health = mean(health, na.rm=TRUE),
                                         habitat = mean(habitat, na.rm=TRUE),
                                         infrastructure = mean(infrastructure, na.rm=TRUE),
                                         water = mean(water, na.rm=TRUE)) %>%
    rename(iso3c = region_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$regions$labels), Name = wbgref$regions$labels), by="iso3c")
    
  # calculate aggregates by income levels
  income_level_aggregates <- df %>%
    group_by(income_level_iso3c) %>% summarize(ecosystems = mean(ecosystems, na.rm=TRUE),
                                         food = mean(food, na.rm=TRUE),
                                         health = mean(health, na.rm=TRUE),
                                         habitat = mean(habitat, na.rm=TRUE),
                                         infrastructure = mean(infrastructure, na.rm=TRUE),
                                         water = mean(water, na.rm=TRUE)) %>%
    rename(iso3c = income_level_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$incomes$labels), Name = wbgref$incomes$labels), by="iso3c")
  
  # merge and select
  df <- df %>%
    bind_rows(region_aggregates, income_level_aggregates) %>%
    filter(iso3c == "BGD" | iso3c == "LMC" | iso3c == "SAS") %>%
    select(Name, ecosystems, food, health, habitat, infrastructure, water)
  
  # rescale
  min <- 0.3
  max <- 0.9
  min_max_norm <- function(x) {
    (x - min) / (max - min)
  }
  df <- df %>%
    mutate(ecosystems = min_max_norm(ecosystems)) %>%
    mutate(food = min_max_norm(food)) %>%
    mutate(health = min_max_norm(health)) %>%
    mutate(habitat = min_max_norm(habitat)) %>%
    mutate(infrastructure = min_max_norm(infrastructure)) %>%
    mutate(water = min_max_norm(water))
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggradar(
        df,
        font.radar = style$family,
        values.radar = c(min, (min+max)/2, max),
        grid.min = 0, grid.mid = 0.5, grid.max = 1,
        grid.label.size = 3,  # Affects the grid annotations (0%, 50%, etc.)
        axis.label.size = 3, # Afftects the names of the variables
        group.point.size = 3   # Simply the size of the point 
      ) +
      style$theme() +
      theme(
        line = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        legend.position = c(1, 0),  
        legend.justification = c(1, 0),
        legend.text = element_text(size = 7, family = style$family),
        legend.key = element_rect(fill = NA, color = NA),
        legend.background = element_blank()
      )
    },
    aspect_ratio = 1,
    title = "Bangladesh's vulnerability in six life-supporting sectors.",
    subtitle = "Vulnerability scores (0-1 lower is better), 2019",
    note = "Note: Vulnerability measures a country's exposure, sensitivity and ability to adapt to the negative impact of climate change.",
    source = "Source: The Notre Dame-Global Adaptation Index (ND-GAIN) Country Index."
  )
}

fig_ch1_vulnerability()

figure_save_draft_png(fig_ch1_vulnerability(), style_SAR_CCDR, "../png/fig_ch1_vulnerability.png", height=4.1, width=4.1)
```



&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Readiness score

Data source: https://gain.nd.edu/our-work/country-index/download-data/

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=4.1, out.width=800, dpi=200}
library(ggradar)
library(showtext)

fig_ch1_readiness <- function() {
  
  # data
  df <- read_csv("../data/readiness.csv")

  # add regions and income levels
  df <- df %>%
    rename(iso3c = ISO3) %>%
    left_join(wbgref$countries$regions, by="iso3c") %>%
    left_join(wbgref$countries$incomegroups, by="iso3c")
  
  # calculate aggregates by regions
  region_aggregates <- df %>%
    group_by(region_iso3c) %>% summarize(economic = mean(economic, na.rm=TRUE),
                                         governance = mean(governance, na.rm=TRUE),
                                         social = mean(social, na.rm=TRUE)) %>%
    rename(iso3c = region_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$regions$labels), Name = wbgref$regions$labels), by="iso3c")
    
  # calculate aggregates by income levels
  income_level_aggregates <- df %>%
    group_by(income_level_iso3c) %>% summarize(economic = mean(economic, na.rm=TRUE),
                                         governance = mean(governance, na.rm=TRUE),
                                         social = mean(social, na.rm=TRUE)) %>%
    rename(iso3c = income_level_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$incomes$labels), Name = wbgref$incomes$labels), by="iso3c")
  
  # merge and select
  df <- df %>%
    bind_rows(region_aggregates, income_level_aggregates) %>%
    filter(iso3c == "BGD" | iso3c == "LMC" | iso3c == "SAS") %>%
    select(Name, economic, governance, social)
  
  # rescale
  min <- 0.2
  max <- 0.45
  min_max_norm <- function(x) {
    (x - min) / (max - min)
  }
  df <- df %>%
    mutate(economic = min_max_norm(economic)) %>%
    mutate(governance = min_max_norm(governance)) %>%
    mutate(social = min_max_norm(social))
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggradar(
        df,
        font.radar = style$family,
        values.radar = c(min, (min+max)/2, max),
        grid.min = 0, grid.mid = 0.5, grid.max = 1,
        grid.label.size = 3,  # Affects the grid annotations (0%, 50%, etc.)
        axis.label.size = 3, # Afftects the names of the variables
        group.point.size = 3   # Simply the size of the point 
      ) +
      style$theme() +
      theme(
        line = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        legend.position = c(1, 0),  
        legend.justification = c(1, 0),
        legend.text = element_text(size = 7, family = style$family),
        legend.key = element_rect(fill = NA, color = NA),
        legend.background = element_blank()
      )
    },
    aspect_ratio = 1,
    title = "Bangladesh's readiness in economic opportunity, governance, and social structures.",
    subtitle = "Readiness scores (0-1 higher is better), 2019",
    note = "Note: Readiness measures a country’s ability to leverage investments and convert them to adaptation actions.",
    source = "Source: The Notre Dame-Global Adaptation Index (ND-GAIN) Country Index."
  )
}

fig_ch1_readiness()

figure_save_draft_png(fig_ch1_readiness(), style_SAR_CCDR, "../png/fig_ch1_readiness.png", height=4.1, width=4.1)

```





&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## ND-GAIN

Data source: https://gain.nd.edu/our-work/country-index/download-data/

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=3.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_nd_gain <- function() {
  
  # data
  df <- read_csv("../data/ND-gain.csv")

  # add regions and income levels
  df <- df %>%
    rename(iso3c = ISO3) %>%
    left_join(wbgref$countries$regions, by="iso3c") %>%
    left_join(wbgref$countries$incomegroups, by="iso3c")

  # calculate aggregates by regions
  region_aggregates <- df %>%
    group_by(region_iso3c) %>% summarise(across(where(is.double), ~ mean(.x, na.rm = TRUE))) %>%
    rename(iso3c = region_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$regions$labels), Name = wbgref$regions$labels), by="iso3c")
  
  # calculate aggregates by income levels
  income_level_aggregates <- df %>%
    group_by(income_level_iso3c) %>% summarise(across(where(is.double), ~ mean(.x, na.rm = TRUE))) %>%
    rename(iso3c = income_level_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$incomes$labels), Name = wbgref$incomes$labels), by="iso3c")
  
  # merge and select
  df <- df %>%
    bind_rows(region_aggregates, income_level_aggregates) %>%
    filter(iso3c == "BGD" | iso3c == "LMC" | iso3c == "SAS") %>%
    select(-c(region_iso3c, income_level_iso3c)) %>%
    gather(key="Year", value="Gain", "1995":"2019") %>%
    select(iso3c, Name, Year, Gain) %>%
    mutate(Year = as.numeric(Year))
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = Year, y = Gain, group = rev(iso3c), color = iso3c)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$Year), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df %>% filter(Year == max(Year)) %>% pull(Gain) %>% repel(gap=6),
            labels = df %>% filter(Year == max(Year)) %>% pull(Name)
          )) +
        scale_color_manual(values = c(
          "LMC" = style$colors$spot.secondary.light, 
          "SAS" = style$colors$spot.secondary.light,
          "BGD" = style$colors$spot.primary)) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Bangladesh's ND-GAIN dropped by nearly 10% points in 2014.",
    subtitle = "ND-GAIN Country Index (0-100 higher is better), 1995-2019",
    note = "Note: The ND-GAIN Country Index summarizes a country's vulnerability to climate change and other global challenges in combination with its readiness to improve resilience.",
    source = "Source: The Notre Dame-Global Adaptation Index (ND-GAIN) Country Index."
  )
}

fig_ch1_nd_gain()

figure_save_draft_png(fig_ch1_nd_gain(), style_SAR_CCDR, "../png/fig_ch1_nd_gain.png", height=3.1, width=5.5)
```







