---
title: "Bangladesh CCDR - 01. Chapter 1"
date: "03/11/2022"
output:
  github_document: default
  html_document: default
knit: (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_format = "github_document");
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_format = "html_document",
                        output_dir=file.path(dirname(inputFile), "../html/"))                  
      })
---

Chapter 1 description

```{r, echo=FALSE, results='hide', message=FALSE}
source("../../styles/SAR_CCDR_style.R")
source("../../utils/CCDR_utils.R")
library(knitr)
library(dplyr)
library(tidyr)
library(tidyverse)
library(stringr)
library(ggplot2)
library(ggalt)
library(forcats)
library(png)
library(ggpubr)
library(ggrepel)
library(scales)
library(hrbrthemes)
library(viridis)
library(wbstats)
library(wbgcharts)
library(wbgmaps)
library(wbggeo)
library(readr)
library(readxl)
library(gtable)
library(grid)
library(lubridate)
library(extrafont)
library(zoo)
create_wbgref()
style = style_SAR_CCDR()
```





&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Economic growth and poverty

Data source: WDI

Indicators: NY.GDP.PCAP.PP.CD

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=3.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_economic_growth <- function() {

  # data
  df <- wb_data(
    indicator = c("NY.GDP.PCAP.PP.CD"),
    country = c("BGD", "LMC", "SAS"),
    start_date = 1990,
    end_date = 2020
  )
  df <- df %>% 
    mutate(num_def = NY.GDP.PCAP.PP.CD) %>% 
    select(iso3c, country, date, num_def) 
  
  # chart
  color_list = c(
    "XN" = style$colors$neutral.dark,
    "SAS" = style$colors$neutral, 
    "BGD" = style$colors$blue)
  
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = date, y = num_def, group = rev(iso3c), color = iso3c)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$date), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df %>% filter(date == max(date)) %>% pull(num_def) %>% repel(gap=6),
            labels = df %>% filter(date == max(date)) %>% pull(country)
          )) +
        scale_color_manual(values = color_list) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Bangladesh's economic growth compared with South Asia and lower-middle-income group",
    subtitle = "GDP per capita, PPP (current international $), 1990 to 2020",
    source = "Source: World Development Indicators (NY.GDP.PCAP.PP.CD)."
  )
}

fig_ch1_economic_growth()

figure_save_draft_png(fig_ch1_economic_growth(), style_SAR_CCDR, "../png/fig_ch1_economic_growth.png", height=3.1, width=5.5)

```


```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=3.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_economic_growth_var1 <- function() {

  # data
  df <- wb_data(
    indicator = c("NY.GDP.PCAP.PP.CD"),
    country = c("BGD", "LMC", "SAS"),
    start_date = 1990,
    end_date = 2020
  )
  df <- df %>% 
    mutate(num_def = NY.GDP.PCAP.PP.CD) %>% 
    select(iso3c, country, date, num_def) 
  
  # chart
  color_list = c(
    "XN" = style$colors$red.light,
    "SAS" = style$colors$purple.light, 
    "BGD" = style$colors$navy)
  
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = date, y = num_def, group = rev(iso3c), color = iso3c)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$date), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df %>% filter(date == max(date)) %>% pull(num_def) %>% repel(gap=6),
            labels = df %>% filter(date == max(date)) %>% pull(country)
          ), 
          expand=c(0.15,0)) +
        scale_color_manual(values = color_list) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Bangladesh's economic growth compared with South Asia and lower-middle-income group",
    subtitle = "GDP per capita, PPP (current international $), 1990 to 2020",
    source = "Source: World Development Indicators (NY.GDP.PCAP.PP.CD)."
  )
}

fig_ch1_economic_growth_var1()

figure_save_draft_png(fig_ch1_economic_growth_var1(), style_SAR_CCDR, "../png/fig_ch1_economic_growth_var1.png", height=3.1, width=5.5)

```



Data source: WDI

Indicators: SI.POV.DDAY

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=3.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_poverty <- function() {

  # data
  df <- wb_data(
    indicator = c("SI.POV.DDAY"),
    country = c("BGD", "LMC", "SAS"),
    start_date = 1990,
    end_date = 2020
  )
  df <- df %>% 
    mutate(poverty = SI.POV.DDAY) %>% 
    select(iso3c, country, date, poverty) 
  df.poverty <- df %>%
    group_by(iso3c) %>% 
    mutate(interp = na.approx(poverty, na.rm=FALSE))
  
  # chart
  color_list = c(
    "XN" = style$colors$neutral.dark,
    "SAS" = style$colors$neutral, 
    "BGD" = style$colors$blue)
  
  figure(
    data = df.poverty,
    plot = function(df.poverty, style = style_SAR_CCDR()) {
      ggplot(df.poverty, aes(x = date, group = rev(iso3c), color = iso3c)) +
        geom_point(aes(y = poverty)) +
        geom_line(aes(y = interp), size = style$linesize/2, linetype = "dotted") +
        geom_line(aes(y = poverty), size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$date), expand=c(0,1)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = c(16, 12.8),
            labels = c("Bangladesh", "Lower middle income")
          )) +
        annotate("text", x = 2013, y = 30, label = "South Asia", size = 2.5, family = style$family, color = style$colors$text) +
        scale_color_manual(values = color_list) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Bangladesh's poverty compared with South Asia and lower-middle-income group",
    subtitle = "Poverty headcount ratio at $1.90 a day (2011 PPP) (% of population)",
    source = "Source: World Development Indicators (SI.POV.DDAY)."
  )
}

fig_ch1_poverty()

figure_save_draft_png(fig_ch1_poverty(), style_SAR_CCDR, "../png/fig_ch1_poverty.png", height=3.1, width=5.5)

```


```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=3.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_poverty_var1 <- function() {

  # data
  df <- wb_data(
    indicator = c("SI.POV.DDAY"),
    country = c("BGD", "LMC", "SAS"),
    start_date = 1990,
    end_date = 2020
  )
  df <- df %>% 
    mutate(poverty = SI.POV.DDAY) %>% 
    select(iso3c, country, date, poverty) 
  df.poverty <- df %>%
    group_by(iso3c) %>% 
    mutate(interp = na.approx(poverty, na.rm=FALSE))
  
  # chart
  color_list = c(
    "XN" = style$colors$red.light,
    "SAS" = style$colors$purple.light, 
    "BGD" = style$colors$navy)
  
  figure(
    data = df.poverty,
    plot = function(df.poverty, style = style_SAR_CCDR()) {
      ggplot(df.poverty, aes(x = date, group = rev(iso3c), color = iso3c)) +
        geom_point(aes(y = poverty)) +
        geom_line(aes(y = interp), size = style$linesize/2, linetype = "dotted") +
        geom_line(aes(y = poverty), size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$date), expand=c(0,1)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = c(16, 12.8),
            labels = c("Bangladesh", "Lower middle income")
          ), 
          expand=c(0.35,0)) +
        annotate("text", x = 2013, y = 30, label = "South Asia", size = 2.5, family = style$family, color = style$colors$text) +
        scale_color_manual(values = color_list) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Bangladesh's poverty compared with South Asia and lower-middle-income group",
    subtitle = "Poverty headcount ratio at $1.90 a day (2011 PPP) (% of population)",
    source = "Source: World Development Indicators (SI.POV.DDAY)."
  )
}

fig_ch1_poverty_var1()

figure_save_draft_png(fig_ch1_poverty_var1(), style_SAR_CCDR, "../png/fig_ch1_poverty_var1.png", height=3.1, width=5.5)

```



Data source: WDI

Indicators: NY.GDP.PCAP.PP.CD, SI.POV.DDAY

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=3.1, fig.width=8.2, out.width=800, dpi=200}

fig_ch1_economic_growth_and_poverty <- function() {

  # data
  df <- wb_data(
    indicator = c("NY.GDP.PCAP.PP.CD", "SI.POV.DDAY"),
    country = c("BGD", "LMC", "SAS"),
    start_date = 1990,
    end_date = 2020
  )
  df <- df %>% 
    mutate(gdp = NY.GDP.PCAP.PP.CD) %>% 
    mutate(poverty = SI.POV.DDAY) %>% 
    select(iso3c, country, date, gdp, poverty)  %>%
    mutate(date = as.numeric(date))
  
  # chart
  color_list = c(
    "XN" = style$colors$neutral.dark,
    "SAS" = style$colors$neutral, 
    "BGD" = style$colors$blue)
  
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      
      df.gdp <- df %>%
        select(iso3c, country, date, gdp) 
      
      p.gdp <- ggplot(df.gdp, aes(x = date, y = gdp, group = rev(iso3c), color = iso3c)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$date), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df.gdp %>% filter(date == max(date)) %>% pull(gdp) %>% repel(gap=6),
            labels = df.gdp %>% filter(date == max(date)) %>% pull(country)
          )) +
        scale_color_manual(values = color_list) +
        labs(subtitle = "GDP per capita, PPP (current international $)")+
        style$theme()
      
      df.poverty <- df %>%
        select(iso3c, country, date, poverty) %>% 
        group_by(iso3c) %>% 
        mutate(interp = na.approx(poverty, na.rm=FALSE))
      
      p.poverty <- ggplot(df.poverty, aes(x = date, group = rev(iso3c), color = iso3c)) +
        geom_point(aes(y = poverty)) +
        geom_line(aes(y = interp), size = style$linesize/2, linetype = "dotted") +
        geom_line(aes(y = poverty), size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$date), expand=c(0,1)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = c(16, 12.8),
            labels = c("Bangladesh", "Lower middle income")
          )) +
        annotate("text", x = 2013, y = 30, label = "South Asia", size = 2.5, family = style$family, color = style$colors$text) +
        scale_color_manual(values = color_list) +
        labs(subtitle = "Poverty headcount ratio at $1.90 a day (2011 PPP) (% of population)")+
        style$theme()
      
      
      pt.gdp <- ggplotGrob(p.gdp)
      pt.poverty <- ggplotGrob(p.poverty)
  
      chart <- gtable_row(
        "chart", 
        list(pt.gdp, zeroGrob(), pt.poverty), 
        height = unit(1, "null"), 
        widths = unit.c(unit(1, "null"), unit(0.3, "in"), unit(1, "null"))
        )
      chart$theme <- style$theme()
      chart
      
    },
    aspect_ratio = 1,
    title = "Bangladesh's economic growth and poverty compared with South Asia and lower-middle-income group",
    source = "Source: World Development Indicators (NY.GDP.PCAP.PP.CD, SI.POV.DDAY)."
  )
}

fig_ch1_economic_growth_and_poverty()

figure_save_draft_png(fig_ch1_economic_growth_and_poverty(), style_SAR_CCDR, "../png/fig_ch1_economic_growth_and_poverty.png", height=3.1, width=8.2)

```


```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=3.1, fig.width=8.2, out.width=800, dpi=200}

fig_ch1_economic_growth_and_poverty_var1 <- function() {

  # data
  df <- wb_data(
    indicator = c("NY.GDP.PCAP.PP.CD", "SI.POV.DDAY"),
    country = c("BGD", "LMC", "SAS"),
    start_date = 1990,
    end_date = 2020
  )
  df <- df %>% 
    mutate(gdp = NY.GDP.PCAP.PP.CD) %>% 
    mutate(poverty = SI.POV.DDAY) %>% 
    select(iso3c, country, date, gdp, poverty)  %>%
    mutate(date = as.numeric(date))
  
  # chart
  color_list = c(
    "XN" = style$colors$red.light,
    "SAS" = style$colors$purple.light, 
    "BGD" = style$colors$navy)
  
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      
      df.gdp <- df %>%
        select(iso3c, country, date, gdp) 
      
      p.gdp <- ggplot(df.gdp, aes(x = date, y = gdp, group = rev(iso3c), color = iso3c)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$date), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df.gdp %>% filter(date == max(date)) %>% pull(gdp) %>% repel(gap=6),
            labels = df.gdp %>% filter(date == max(date)) %>% pull(country)
          ), 
          expand=c(0.15,0)) +
        scale_color_manual(values = color_list) +
        labs(subtitle = "GDP per capita, PPP (current international $)")+
        style$theme()
      
      df.poverty <- df %>%
        select(iso3c, country, date, poverty) %>% 
        group_by(iso3c) %>% 
        mutate(interp = na.approx(poverty, na.rm=FALSE))
      
      p.poverty <- ggplot(df.poverty, aes(x = date, group = rev(iso3c), color = iso3c)) +
        geom_point(aes(y = poverty)) +
        geom_line(aes(y = interp), size = style$linesize/2, linetype = "dotted") +
        geom_line(aes(y = poverty), size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$date), expand=c(0,1)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = c(16, 12.8),
            labels = c("Bangladesh", "Lower middle income")
          ), 
          expand=c(0.35,0)) +
        annotate("text", x = 2013, y = 30, label = "South Asia", size = 2.5, family = style$family, color = style$colors$text) +
        scale_color_manual(values = color_list) +
        labs(subtitle = "Poverty headcount ratio at $1.90 a day (2011 PPP) (% of population)")+
        style$theme()
      
      
      pt.gdp <- ggplotGrob(p.gdp)
      pt.poverty <- ggplotGrob(p.poverty)
  
      chart <- gtable_row(
        "chart", 
        list(pt.gdp, zeroGrob(), pt.poverty), 
        height = unit(1, "null"), 
        widths = unit.c(unit(1, "null"), unit(0.3, "in"), unit(1, "null"))
        )
      chart$theme <- style$theme()
      chart
      
    },
    aspect_ratio = 1,
    title = "Bangladesh's economic growth and poverty compared with South Asia and lower-middle-income group",
    source = "Source: World Development Indicators (NY.GDP.PCAP.PP.CD, SI.POV.DDAY)."
  )
}

fig_ch1_economic_growth_and_poverty_var1()

figure_save_draft_png(fig_ch1_economic_growth_and_poverty_var1(), style_SAR_CCDR, "../png/fig_ch1_economic_growth_and_poverty_var1.png", height=3.1, width=8.2)

```





&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Structure of economy

Data source: WDI

Indicators: "NV.AGR.TOTL.ZS", "NV.IND.TOTL.ZS", "NV.SRV.TOTL.ZS", "SL.AGR.EMPL.ZS", "SL.IND.EMPL.ZS", "SL.SRV.EMPL.ZS", "SL.AGR.EMPL.MA.ZS", "SL.IND.EMPL.MA.ZS", "SL.SRV.EMPL.MA.ZS", "SL.AGR.EMPL.FE.ZS", "SL.IND.EMPL.FE.ZS", "SL.SRV.EMPL.FE.ZS"

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=8.5, out.width=800, dpi=200}

fig_ch1_structure_of_economy <- function() {
  
# data
country_code = "BGD"
columns = c("iso2c", "iso3c", "country", "year", "Agriculture", "Industry", "Services")

indicators <- c("NV.AGR.TOTL.ZS", "NV.IND.TOTL.ZS", "NV.SRV.TOTL.ZS")
year <- 2020
df.nv <- wb_data(
  indicator = indicators,
  country = country_code,
  start_date = year,
  end_date = year
)

names(df.nv) = columns
for (x in colnames(df.nv)) attr(df.nv[[x]], "label") <- NULL
df.nv$indicator = "value added (% of GDP)"
 
indicators <- c("SL.AGR.EMPL.ZS", "SL.IND.EMPL.ZS", "SL.SRV.EMPL.ZS")
year <- 2019
df.empl <- wb_data(
  indicator = indicators,
  country = country_code,
  start_date = year,
  end_date = year
)

names(df.empl) = columns
for (x in colnames(df.empl)) attr(df.empl[[x]], "label") <- NULL
df.empl$indicator = "% of employment (modeled ILO estimate)"

indicators <- c("SL.AGR.EMPL.MA.ZS", "SL.IND.EMPL.MA.ZS", "SL.SRV.EMPL.MA.ZS")
year <- 2019
df.ma <- wb_data(
  indicator = indicators,
  country = country_code,
  start_date = year,
  end_date = year
)

names(df.ma) = columns
for (x in colnames(df.ma)) attr(df.ma[[x]], "label") <- NULL
df.ma$indicator = "% of male employment (modeled ILO estimate)"

indicators <- c("SL.AGR.EMPL.FE.ZS", "SL.IND.EMPL.FE.ZS", "SL.SRV.EMPL.FE.ZS")
year <- 2019
df.fe <- wb_data(
  indicator = indicators,
  country = country_code,
  start_date = year,
  end_date = year
)

names(df.fe) = columns
for (x in colnames(df.fe)) attr(df.fe[[x]], "label") <- NULL
df.fe$indicator = "% of female employment (modeled ILO estimate)"

df <- bind_rows(df.nv, df.empl, df.ma, df.fe) %>%
  gather(sector, value, c(Agriculture, Industry, Services)) %>%
  mutate(year = as.numeric(year))

# chart
indicator_labels = c("value added (% of GDP)", "% of employment (modeled ILO estimate)", "% of male employment (modeled ILO estimate)", "% of female employment (modeled ILO estimate)")
figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = "", y = value, fill = sector)) +
        geom_bar(width = 1, stat = "identity") +
        scale_fill_manual(values = c(
          Agriculture = style$colors$spot.secondary,
          Industry = style$colors$spot.primary.light,
          Services = style$colors$spot.primary
        )) +
        # geom_text(aes(y = ypos, label = sector), color = "white", size=2) +
        facet_grid(cols = vars(factor(indicator, levels=indicator_labels))) +
        # facet_grid(indicator ~ .) +
        # facet_grid(iso3c ~ ., labeller = as_labeller(str_wrap_lines(wbgref$regions$labels,3,force=TRUE))) + 
        coord_polar(theta = "y") +
        style$theme() +
        style$theme_legend("bottom") +
        theme(
          axis.text = element_blank(),
          panel.grid  = element_blank(),
          strip.text.x = element_text(angle = 0, hjust = 0.5),
          panel.spacing = unit(0, "npc")
        )
    },
    title = "Structure of ecomony in Bangladesh",
    subtitle = "Industry value added (2020) and employment breakdown (2019)",
    source = "Source: World Development Indicators"
  )
}

fig_ch1_structure_of_economy()

figure_save_draft_png(fig_ch1_structure_of_economy(), style_SAR_CCDR, "../png/fig_ch1_structure_of_economy.png", height=4.1, width=8.5)
```


```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=8.5, out.width=800, dpi=200}

fig_ch1_structure_of_economy_var1 <- function() {
  
  # data
  country_code = "BGD"
  columns = c("iso2c", "iso3c", "country", "year", "Agriculture", "Industry", "Services")
  
  indicators <- c("NV.AGR.TOTL.ZS", "NV.IND.TOTL.ZS", "NV.SRV.TOTL.ZS")
  year <- 2020
  df.nv <- wb_data(
    indicator = indicators,
    country = country_code,
    start_date = year,
    end_date = year
  )
  
  names(df.nv) = columns
  for (x in colnames(df.nv)) attr(df.nv[[x]], "label") <- NULL
  df.nv$indicator = "value added (% of GDP)"
   
  indicators <- c("SL.AGR.EMPL.ZS", "SL.IND.EMPL.ZS", "SL.SRV.EMPL.ZS")
  year <- 2019
  df.empl <- wb_data(
    indicator = indicators,
    country = country_code,
    start_date = year,
    end_date = year
  )
  
  names(df.empl) = columns
  for (x in colnames(df.empl)) attr(df.empl[[x]], "label") <- NULL
  df.empl$indicator = "% of employment (modeled ILO estimate)"
  
  indicators <- c("SL.AGR.EMPL.MA.ZS", "SL.IND.EMPL.MA.ZS", "SL.SRV.EMPL.MA.ZS")
  year <- 2019
  df.ma <- wb_data(
    indicator = indicators,
    country = country_code,
    start_date = year,
    end_date = year
  )
  
  names(df.ma) = columns
  for (x in colnames(df.ma)) attr(df.ma[[x]], "label") <- NULL
  df.ma$indicator = "% of male employment (modeled ILO estimate)"
  
  indicators <- c("SL.AGR.EMPL.FE.ZS", "SL.IND.EMPL.FE.ZS", "SL.SRV.EMPL.FE.ZS")
  year <- 2019
  df.fe <- wb_data(
    indicator = indicators,
    country = country_code,
    start_date = year,
    end_date = year
  )
  
  names(df.fe) = columns
  for (x in colnames(df.fe)) attr(df.fe[[x]], "label") <- NULL
  df.fe$indicator = "% of female employment (modeled ILO estimate)"
  
  df <- bind_rows(df.nv, df.empl, df.ma, df.fe) %>%
    gather(sector, value, c(Agriculture, Industry, Services)) %>%
    mutate(year = as.numeric(year)) %>%
    arrange(desc(sector), desc(value)) %>%
    group_by(indicator) %>%
    mutate(pos = cumsum(value)- value/2)
  
  # chart
  color_list = c(
    Agriculture = style$colors$red,
    Industry = style$colors$orange,
    Services = style$colors$blue
  )
  
  indicator_labels = c("value added (% of GDP)", "% of employment (modeled ILO estimate)", "% of male employment (modeled ILO estimate)", "% of female employment (modeled ILO estimate)")
  
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = factor(1), y = value, fill = sector)) +
        geom_bar(width = 1, stat = "identity", color = "white", size=1) +
        scale_fill_manual(values = color_list) +
        # geom_text(aes(y = ypos, label = sector), color = "white", size=2) +
        geom_text(aes(x= factor(1), y=pos, label = paste0(round(value), "%")), size=3, family=style$family) +
        facet_grid(cols = vars(factor(indicator, levels=indicator_labels))) +
        # facet_grid(indicator ~ .) +
        # facet_grid(iso3c ~ ., labeller = as_labeller(str_wrap_lines(wbgref$regions$labels,3,force=TRUE))) + 
        coord_polar(theta = "y") +
        style$theme() +
        style$theme_legend("bottom") +
        theme(
          panel.grid  = element_blank(),
          strip.text.x = element_text(angle = 0, hjust = 0.5),
          panel.spacing = unit(0, "npc"),
          axis.text = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank()
        )
    },
    title = "Structure of ecomony in Bangladesh",
    subtitle = "Industry value added (2020) and employment breakdown (2019)",
    source = "Source: World Development Indicators"
  )
}

fig_ch1_structure_of_economy_var1()

figure_save_draft_png(fig_ch1_structure_of_economy_var1(), style_SAR_CCDR, "../png/fig_ch1_structure_of_economy_var1.png", height=4.1, width=8.5)
```






&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Total energy supply (TES)

Data source: https://www.iea.org/data-and-statistics/data-browser/?country=BANGLADESH&fuel=Energy%20supply&indicator=TESbySource

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=6.5, out.width=800, dpi=200}

fig_ch1_TES_share_by_source <- function() {
  
  # data
  df <- read_csv("../data/Total energy supply (TES) by source - Bangladesh.csv", skip=4) %>%
    rename(year = X1) %>%
    select(-Units)
  df <- df %>%
    gather(source, TJ, 2:7) %>%
    group_by(year) %>%
    mutate(percentage =  100 *TJ/sum(TJ, na.rm=TRUE)) %>%
    mutate(year = as.numeric(year))
  
  ordered_source <- df %>%
    filter(year == 2019) %>%
    arrange(desc(percentage),source) %>% pull(source)
  
  # plot
  color_list <- c("Natural gas" = "#227C9D",
                  "Biofuels and waste" = "#45462A", 
                  "Oil" = "#BCAA99", 
                  "Coal" = "#443850", 
                  "Hydro" = "#3AAFB9",
                  "Wind, solar, etc." = "#BBBE64")
  
  figure(
    data = df,
    plot = function(data, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = year, y = percentage, fill = factor(source, levels = ordered_source))) +
        geom_area() +
        style$theme() + 
        style$theme_legend("right") +
        scale_x_continuous(expand = c(0, 1)) +
        # scale_y_continuous(labels = millions()) +
        scale_fill_manual(values=color_list)
      },
      aspect_ratio = 1.5,
      title = paste0("Natural gas provide 59% of total energy supply, followed by Biofuels and waste, oil, and coal."),
      subtitle = "Total energy supply (TES) by source (%), 1990-2019",
      note = "Note: TES is made up of production + imports - exports - international marine bunkers - international aviation bunkers ± stock changes.",
      source = "Source: IEA World Energy Balances https://www.iea.org/data-and-statistics/data-product/world-energy-statistics-and-balances"
  )
}

fig_ch1_TES_share_by_source()

figure_save_draft_png(fig_ch1_TES_share_by_source(), style_SAR_CCDR, "../png/fig_ch1_TES_share_by_source.png", height=4.1, width=6.5)

```






&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Natural disasters

Data source: https://ourworldindata.org/natural-disasters

Country: Bangladesh

Disaster type: All disasters (by type)

Impact: Deaths, Economic damages (%GDP)

Timespan: Decadal average

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=5.5, out.width=800, dpi=200}
fig_ch1_natural_disasters <- function() {
  
  # data
  df1 <- read_csv("../data/natural-disasters_bangladesh_deaths.csv")
  names(df1) <- c('Entity', 'Code', 'Year', 'Extreme temperature', 'Wildfires', 'Storms', 
                  'Landslides', 'Mass movement (dry)', 'Volcanic activity', 'Earthquakes', 'Floods', 'Drought')
  df1 <- df1 %>%
    select(-c('Wildfires', 'Mass movement (dry)', 'Volcanic activity')) %>%
    gather(Type, Deaths, 4:9) %>%
    select(Year, Type, Deaths)
  
  df2 <- read_csv("../data/natural-disasters_bangladesh_gdp.csv")
  names(df2) <- c('Entity', 'Code', 'Year', 'Extreme temperature', 'Wildfires', 'Storms', 
                  'Landslides', 'Mass movement (dry)', 'Volcanic activity', 'Earthquakes', 'Floods', 'Drought')
  df2 <- df2 %>%
    select(-c('Wildfires', 'Mass movement (dry)', 'Volcanic activity')) %>%
    gather(Type, Damage, 4:9) %>%
    mutate(Damage = Damage*100) %>%
    select(Year, Type, Damage)
  
  df <- merge(df1, df2, by=c("Year", "Type"))
  
  # chart
  figure(
    data =  df,
    plot = function(df, style = style_SAR_CCDR()) {
      p <- ggplot(df, aes(x=Year, y=reorder(Type, desc(Type)), size=ifelse(Damage==0, NA, Damage), color=Deaths, fill=Deaths)) +
        geom_point(alpha=0.5, shape=21, color="black") +
        scale_size(range = c(1, 20), name="Damage (%GDP)",
                   breaks = c(10, 50,100),
                   labels = c("10", "50", "100")) +
        scale_fill_distiller(palette = "Spectral") + 
        scale_x_continuous(limits = c(1960, 2012), breaks = c(1960, 1970, 1980, 1990, 2000, 2010), labels = c("1960-1969", "1970-1979", "1980-1989", "1990-1999", "2000-2009", "2010-2019")) +
        xlab("Year") +
        ylab("Natural Disasters") +
        geom_curve(aes(x = 1975, y = 1.7, xend = 1970, yend = 1.3), 
                               colour = "#555555", 
                               size=0.3, 
                               curvature = 0.2,
                               arrow = arrow(length = unit(0.03, "npc"))) +
        annotate("text", x = 1975, y = 1.9, label = "including 1970 Bhola cyclone", size = 2.5, family = style$family) +
        style$theme() +
        theme(
          axis.title.x = element_text(vjust = -5),
          axis.title.y = element_text(angle = 90, vjust = 0, margin = margin(r = 15)),
          axis.text.x = element_text(angle = 0, vjust = 2), 
          legend.title = element_text(),
          legend.box.just = "center",
          legend.position = "right"
        )
    },
    aspect_ratio = 1,
    title = "Floods and storms are the most damaging natural disasters in Bangladesh",
    subtitle = "Decadal average: Number of deaths and economic damages (% GDP) from natural disasters",
    note = "Note: Decadal figures are measured as the annual average over the subsequent ten-year period.",
    source = "Source: Our World in Data."
  )
}

fig_ch1_natural_disasters()

figure_save_draft_png(fig_ch1_natural_disasters(), style_SAR_CCDR, "../png/fig_ch1_natural_disasters.png", height=4.1, width=5.5)
```






Data source: https://public.emdat.be/data

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=5.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_natural_disaster_frequency <- function() {
  
  # data
  df <- read_excel("../data/emdat_public_2022_03_14_Bangladesh.xlsx", skip=6) %>%
    filter(Year >= 2000) %>%
    select(`Disaster Subgroup`, `Disaster Type`, `Total Deaths`, `Total Damages, Adjusted ('000 US$)`) %>% 
    rename(category = `Disaster Subgroup`) %>%
    rename(type = `Disaster Type`)
  
  df.category <- df %>%
    group_by(category) %>%
    summarise(category_frequency = n(),
              category_deaths = sum(`Total Deaths`, na.rm=TRUE),
              category_damage = sum(`Total Damages, Adjusted ('000 US$)`, na.rm=TRUE)) %>%
    mutate(percentage_frequency =  100 *category_frequency/sum(category_frequency, na.rm=TRUE)) %>%
    mutate(percentage_deaths =  100 *category_deaths/sum(category_deaths, na.rm=TRUE)) %>%
    mutate(percentage_damage =  100 *category_damage/sum(category_damage, na.rm=TRUE)) 

  df.type <- df %>%
    group_by(category, type) %>%
    summarise(frequency = n(),
              deaths = sum(`Total Deaths`, na.rm=TRUE),
              damage = sum(`Total Damages, Adjusted ('000 US$)`, na.rm=TRUE),
              .groups = 'drop') %>%
    inner_join(df.category, by="category") 
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      
      df.category <- df.category %>%
        arrange(desc(category_frequency))
      df.category$ymax <- cumsum(df.category$category_frequency)
      df.category$ymin <- c(0, head(df.category$ymax, n=-1))
      df.category$labelPosition <- (df.category$ymax + df.category$ymin) / 2
      df.category$labelPosition <- c(39.5, 101.5, 125, 136.5, 138.5)
      df.category$label <- paste0(df.category$category, "\n(", df.category$category_frequency, ")")
      df.category$label <- c("Meteorological\n(79)", "Hydrological\n(45)", "Biological\n(9)", "Geophysical\n(5)", "" )
      
      df.type <- df.type %>%
        arrange(desc(category_frequency), desc(frequency))
      df.type$ymax <- cumsum(df.type$frequency)
      df.type$ymin <- c(0, head(df.type$ymax, n=-1))
      df.type$labelPosition <- (df.type$ymax + df.type$ymin) / 2
      df.type$angle <- ifelse(df.type$labelPosition/max(df.type$ymax)*360 < 180, 
                              90 - df.type$labelPosition/max(df.type$ymax)*360, 
                              df.type$labelPosition/max(df.type$ymax)*360*-1 + 270)
      df.type$label <- paste0(df.type$type)
      df.type$label <- c("Storm", "Extrm temp", "Flood", "Landslide", "Epidemic", "Earthquake", "")
      df.type$hjust <- c(0, 1, 1, 1, 1, 1, 1)
  
      ggplot() +
      geom_rect(data=df.category, aes(ymax=ymax, ymin=ymin, xmax=3.5, xmin=2, fill=category), color = "white", size=1) +
      geom_rect(data=df.type, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3.5, fill=category), color = "white", size=1, alpha = 0.4) +
      # geom_text_repel(data = df.category, x=2.6, aes(y = labelPosition, label = label, family=style$family), size=3, box.padding = unit(0, "lines"), 
      #                 show.legend = F, nudge_x = 0) +
      geom_text(data = df.category, x=2.8, aes(y = labelPosition, label = label, family=style$family), size=3) +
      geom_text(data = df.type, x=4.1, aes(y = labelPosition, label = label, angle=angle, hjust=hjust, family=style$family), size=2.5, show.legend = F) + 
      coord_polar(theta="y") +
      xlim(c(1, 4.5)) +
      scale_fill_manual(values = c(
      "Hydrological" = "#07A0C3", 
      "Meteorological" = "#4D8B31",   
      "Geophysical" = "#EF476F",   
      "Biological" = "#F0C808",   
      "Climatological" = "#A15E49"))+
      annotate(geom = 'text', x = 1, y = 0, label = "Frequency") +
      style$theme() +
      theme(legend.position = "none",
            panel.grid.major.x = element_blank(),
            panel.grid.major.y = element_blank(),
            axis.text = element_blank(),
            axis.text.x = element_blank(),
            axis.text.y = element_blank())
    },
    aspect_ratio = 1,
    title = "Natural disasters in recent years",
    subtitle = "Frequency of natural disasters by type, 2000-2022",
    source = "Source: The international disasters database"
  )
}

fig_ch1_natural_disaster_frequency()

figure_save_draft_png(fig_ch1_natural_disaster_frequency(), style_SAR_CCDR, "../png/fig_ch1_natural_disaster_frequency.png", height=5.1, width=5.5)
```



```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=5.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_natural_disaster_deaths <- function() {
  
  # data
  df <- read_excel("../data/emdat_public_2022_03_14_Bangladesh.xlsx", skip=6) %>%
    filter(Year >= 2000) %>%
    select(`Disaster Subgroup`, `Disaster Type`, `Total Deaths`, `Total Damages, Adjusted ('000 US$)`) %>% 
    rename(category = `Disaster Subgroup`) %>%
    rename(type = `Disaster Type`)
  
  df.category <- df %>%
    group_by(category) %>%
    summarise(category_frequency = n(),
              category_deaths = sum(`Total Deaths`, na.rm=TRUE),
              category_damage = sum(`Total Damages, Adjusted ('000 US$)`, na.rm=TRUE)) %>%
    mutate(percentage_frequency =  100 *category_frequency/sum(category_frequency, na.rm=TRUE)) %>%
    mutate(percentage_deaths =  100 *category_deaths/sum(category_deaths, na.rm=TRUE)) %>%
    mutate(percentage_damage =  100 *category_damage/sum(category_damage, na.rm=TRUE)) 

  df.type <- df %>%
    group_by(category, type) %>%
    summarise(frequency = n(),
              deaths = sum(`Total Deaths`, na.rm=TRUE),
              damage = sum(`Total Damages, Adjusted ('000 US$)`, na.rm=TRUE),
              .groups = 'drop') %>%
    inner_join(df.category, by="category") 
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      
      df.category <- df.category %>%
        arrange(desc(category_deaths))
      df.category$ymax <- cumsum(df.category$category_deaths)
      df.category$ymin <- c(0, head(df.category$ymax, n=-1))
      df.category$labelPosition <- (df.category$ymax + df.category$ymin) / 2
      # df.category$labelPosition <- c(37202.5, 76007.0, 85776.0, 85784.5, 85764.5)
      df.category$label <- paste0(df.category$category, "\n(", prettyNum(df.category$category_deaths,big.mark=","), ")")
      df.category$label <- c("Meteorological\n(7,762)","Hydrological\n(3,600)","Biological\n(260)","","" )
      
      df.type <- df.type %>%
        arrange(desc(category_deaths), desc(deaths))
      df.type$ymax <- cumsum(df.type$deaths)
      df.type$ymin <- c(0, head(df.type$ymax, n=-1))
      df.type$labelPosition <- (df.type$ymax + df.type$ymin) / 2
      df.type$angle <- ifelse(df.type$labelPosition/max(df.type$ymax)*360 < 180, 
                              90 - df.type$labelPosition/max(df.type$ymax)*360, 
                              df.type$labelPosition/max(df.type$ymax)*360*-1 + 270)
      df.type$label <- paste0(df.type$type)
      df.type$label <- c("Storm", "Extreme temperature", "Flood", "Landslide", "Epidemic", "", "")
      df.type$hjust <- c(0, 1, 1, 1, 1, 1, 1)

  
      ggplot() +
      geom_rect(data=df.category, aes(ymax=ymax, ymin=ymin, xmax=3.5, xmin=2, fill=category), color = "white", size=1) +
      geom_rect(data=df.type, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3.5, fill=category), color = "white", size=1, alpha = 0.4) +
      # geom_text_repel(data = df.category, x=2.6, aes(y = labelPosition, label = label, family=style$family), size=3, box.padding = unit(0, "lines"), 
      #                 show.legend = F, nudge_x = 0.5, nudge_y = 0.5) +
      geom_text(data = df.category, x=2.7, aes(y = labelPosition, label = label, family=style$family), size=3) +
      geom_text(data = df.type, x=4.1, aes(y = labelPosition, label = label, angle=angle, hjust=hjust, family=style$family), size=2.5, show.legend = F) + 
      coord_polar(theta="y") +
      xlim(c(1, 4.5)) +
      scale_fill_manual(values = c(
      "Hydrological" = "#07A0C3", 
      "Meteorological" = "#4D8B31",   
      "Geophysical" = "#EF476F",   
      "Biological" = "#F0C808",   
      "Climatological" = "#A15E49"))+
      annotate(geom = 'text', x = 1, y = 0, label = "Deaths") +
      style$theme() +
      theme(legend.position = "none",
            panel.grid.major.x = element_blank(),
            panel.grid.major.y = element_blank(),
            axis.text = element_blank(),
            axis.text.x = element_blank(),
            axis.text.y = element_blank())
    },
    aspect_ratio = 1,
    title = "Natural disasters in recent years",
    subtitle = "Total deaths from natural disasters by type, 2000-2022",
    source = "Source: The international disasters database"
  )
}

fig_ch1_natural_disaster_deaths()

figure_save_draft_png(fig_ch1_natural_disaster_deaths(), style_SAR_CCDR, "../png/fig_ch1_natural_disaster_deaths.png", height=5.1, width=5.5)
```


```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=5.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_natural_disaster_damage <- function() {
  
  # data
  df <- read_excel("../data/emdat_public_2022_03_14_Bangladesh.xlsx", skip=6) %>%
    filter(Year >= 2000) %>%
    select(`Disaster Subgroup`, `Disaster Type`, `Total Deaths`, `Total Damages, Adjusted ('000 US$)`) %>% 
    rename(category = `Disaster Subgroup`) %>%
    rename(type = `Disaster Type`)
  
  df.category <- df %>%
    group_by(category) %>%
    summarise(category_frequency = n(),
              category_deaths = sum(`Total Deaths`, na.rm=TRUE),
              category_damage = sum(`Total Damages, Adjusted ('000 US$)`, na.rm=TRUE)) %>%
    mutate(percentage_frequency =  100 *category_frequency/sum(category_frequency, na.rm=TRUE)) %>%
    mutate(percentage_deaths =  100 *category_deaths/sum(category_deaths, na.rm=TRUE)) %>%
    mutate(percentage_damage =  100 *category_damage/sum(category_damage, na.rm=TRUE)) 

  df.type <- df %>%
    group_by(category, type) %>%
    summarise(frequency = n(),
              deaths = sum(`Total Deaths`, na.rm=TRUE),
              damage = sum(`Total Damages, Adjusted ('000 US$)`, na.rm=TRUE),
              .groups = 'drop') %>%
    inner_join(df.category, by="category") 
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      
      df.category <- df.category %>%
        arrange(desc(category_damage))
      df.category$ymax <- cumsum(df.category$category_damage)
      df.category$ymin <- c(0, head(df.category$ymax, n=-1))
      df.category$labelPosition <- (df.category$ymax + df.category$ymin) / 2
      df.category$label <- paste0(df.category$category, "\n(", prettyNum(df.category$category_damage,big.mark=","), ")")
      df.category$label <- c("Hydrological\n(5,787,291)", "Meteorological\n(5,674,392)", "Geophysical\n(717,294)", "", "")
      
      df.type <- df.type %>%
        arrange(desc(category_damage), desc(damage))
      df.type$ymax <- cumsum(df.type$damage)
      df.type$ymin <- c(0, head(df.type$ymax, n=-1))
      df.type$labelPosition <- (df.type$ymax + df.type$ymin) / 2
      df.type$angle <- ifelse(df.type$labelPosition/max(df.type$ymax)*360 < 180,
                              90 - df.type$labelPosition/max(df.type$ymax)*360,
                              df.type$labelPosition/max(df.type$ymax)*360*-1 + 270)
      df.type$label <- paste0(df.type$type)
      df.type$label <- c("Flood", "", "Storm", "", "Earthquake", "","")
      df.type$hjust <- c(0, 1, 1, 1, 1, 1, 1)

  
      ggplot() +
      geom_rect(data=df.category, aes(ymax=ymax, ymin=ymin, xmax=3.5, xmin=2, fill=category), color = "white", size=1) +
      geom_rect(data=df.type, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3.5, fill=category), color = "white", size=1, alpha = 0.4) +
      geom_text(data = df.category, x=2.7, aes(y = labelPosition, label = label, family=style$family), size=3, box.padding = unit(0, "lines"), 
                      show.legend = F) +
      geom_text(data = df.type, x=4.1, aes(y = labelPosition, label = label, angle=angle, hjust=hjust, family=style$family), size=2.5, show.legend = F) + 
      coord_polar(theta="y") +
      xlim(c(1, 4.5)) +
      scale_fill_manual(values = c(
      "Hydrological" = "#07A0C3", 
      "Meteorological" = "#4D8B31",   
      "Geophysical" = "#EF476F",   
      "Biological" = "#F0C808",   
      "Climatological" = "#A15E49"))+
      annotate(geom = 'text', x = 1, y = 0, label = "Damage") +
      style$theme() +
      theme(legend.position = "none",
            panel.grid.major.x = element_blank(),
            panel.grid.major.y = element_blank(),
            axis.text = element_blank(),
            axis.text.x = element_blank(),
            axis.text.y = element_blank())
    },
    aspect_ratio = 1,
    title = "Natural disasters in recent years",
    subtitle = "Total damages from natural disasters by type, Adjusted ('000 US$), 2000-2022",
    source = "Source: The international disasters database"
  )
}

fig_ch1_natural_disaster_damage()

figure_save_draft_png(fig_ch1_natural_disaster_damage(), style_SAR_CCDR, "../png/fig_ch1_natural_disaster_damage.png", height=5.1, width=5.5)
```





&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## National GHG Emission Profile 

https://www.climatewatchdata.org/ghg-emissions?breakBy=sector&chartType=area&end_year=2018&regions=BGD&sectors=total-including-lucf&start_year=1990

Source: CAIT

Country: Bangladesh

Sector: Total including LUCF

Gases: All GHG

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=5.1, fig.width=5.5, out.width=800, dpi=200}
fig_ch1_greenhouse_gas_emissions <- function() {
  
  # data
  df <- read_csv("../data/ghg-emissions.csv")
  df <- head(df, - 2)
  df <- df %>%
    gather(key="Year", value="Emissions", "2018":"1990") %>%
    select(Sector, Year, Emissions) %>%
    mutate(Year = as.numeric(Year))
  
  # chart
  color_list = c(
    "Agriculture" = style$colors$navy, 
    "Energy" = style$colors$blue,   
    "Industrial Processes" = style$colors$neutral.light,
    "Land-Use Change and Forestry" = style$colors$neutral,
    "Waste" = style$colors$neutral)
  
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = Year, y = Emissions, group = Sector, color = Sector)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$Year), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df %>% filter(Year == max(Year)) %>% pull(Emissions) %>% repel(gap=6),
            labels = df %>% filter(Year == max(Year)) %>% pull(Sector)
          )) +
        scale_color_manual(values = color_list, labels = unique(df$Sector)) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Agriculture and energy sectors take up the largest portions of greenhouse gas emissions in Bangladesh",
    subtitle = "Historical Country Greenhouse Gas Emissions (MtCO2e), 1990-2018",
    source = "Source: Climate Watch Historical Country Greenhouse Gas Emissions Data (1990-2018)."
  )
}

fig_ch1_greenhouse_gas_emissions()

figure_save_draft_png(fig_ch1_greenhouse_gas_emissions(), style_SAR_CCDR, "../png/fig_ch1_greenhouse_gas_emissions.png", height=5.1, width=5.5)
```




```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=5.1, fig.width=5.5, out.width=800, dpi=200}
fig_ch1_GHG_emissions_area <- function() {
  
  # data
  df <- read_csv("../data/ghg-emissions.csv")
  df <- head(df, - 2)
  df <- df %>%
    gather(key="Year", value="Emissions", "2018":"1990") %>%
    select(Sector, Year, Emissions) %>%
    mutate(Year = as.numeric(Year)) %>%
    group_by(Year) %>%
    mutate(percentage =  100 *Emissions/sum(Emissions, na.rm=TRUE))
  
    
  ordered_sector <- df %>%
    filter(Year == 2018) %>%
    arrange(desc(percentage)) %>% pull(Sector)
  
  # chart
  color_list = c(
    "Agriculture" = style$colors$orange,  
    "Energy" = style$colors$blue, 
    "Land-Use Change and Forestry" = style$colors$red,
    "Waste" = style$colors$purple,
    "Industrial Processes" = style$colors$navy)
  
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = Year, y = Emissions, fill = factor(Sector, levels=ordered_sector))) +
        geom_area() +
        scale_x_continuous(breaks = bracketed_breaks(df$Year), expand=c(0,0)) +
        scale_y_continuous(
          position="left"
        ) +
        scale_fill_manual(values = color_list) +
        style$theme() +
        style$theme_legend("right")
    },
    aspect_ratio = 1,
    title = "Emissions are primarily from energy and agriculture, comprising 40% and 39% respectively, followed by Land-Use Change and Forestry (9.9%), Waste (9.3%), and Industrial Processes (1.8%).",
    subtitle = "Historical Country Greenhouse Gas Emissions (MtCO2e), 1990-2018",
    source = "Source: Climate Watch Historical Country Greenhouse Gas Emissions Data (1990-2018)."
  )
}

fig_ch1_GHG_emissions_area()

figure_save_draft_png(fig_ch1_GHG_emissions_area(), style_SAR_CCDR, "../png/fig_ch1_GHG_emissions_area.png", height=5.1, width=5.5)
```




```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=5.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_GHG_emissions_pie <- function() {
  
  # data
  df <- read_csv("../data/ghg-emissions.csv")
  df <- head(df, - 2)
  df <- df %>%
    gather(key="Year", value="Emissions", "2018":"1990") %>%
    select(Sector, Year, Emissions) %>%
    mutate(Year = as.numeric(Year)) %>%
    group_by(Year) %>%
    mutate(percentage = 100 *Emissions/sum(Emissions, na.rm=TRUE)) %>%
    filter(Year == 2018) %>%
    arrange(desc(percentage))
  
  df$ymax <- cumsum(df$percentage)
  df$ymin <- c(0, head(df$ymax, n=-1))
  df$labelPosition <- (df$ymax + df$ymin) / 2
  df$label <- paste0(df$Sector, "\n", round(df$percentage,1), "%")
  df$label <- c("Agriculture\n40.1%", "Energy\n38.9%", "Land-Use Change\nand Forestry\n9.9%", "Waste\n9.3%", "Industrial Processes\n1.8%")
  df$vjust <- c(0.5, 0.5, 0.5, 0.7, 0.7)
  
  # chart
  color_list = c(
    "Energy" = style$colors$blue,   
    "Agriculture" = style$colors$orange,  
    "Industrial Processes" = style$colors$navy, 
    "Waste" = style$colors$purple,
    "Land-Use Change and Forestry" = style$colors$red)
    
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=Sector)) +
      geom_rect() +
      geom_label(x=4.5, aes(y=labelPosition, label=label, vjust=vjust), size=2.5, label.size = NA, fill = NA) +
      coord_polar(theta="y") +
      xlim(c(2, 4.5)) +
      scale_fill_manual(values = color_list) +
      # theme_void() +
      style$theme() +
      theme(legend.position = "none",
            panel.grid.major.x = element_blank(),
            panel.grid.major.y = element_blank(),
            axis.text = element_blank(),
            axis.text.x = element_blank(),
            axis.text.y = element_blank(),
            plot.margin = margin(-5,1,-10,1, unit = "mm"))
    },
    aspect_ratio = 1,
    title = "Emissions are primarily from energy and agriculture, comprising 40% and 39% respectively, followed by Land-Use Change and Forestry (9.9%), Waste (9.3%), and Industrial Processes (1.8%).",
    subtitle = "Historical Country Greenhouse Gas Emissions (MtCO2e), 2018",
    source = "Source: Climate Watch Historical Country Greenhouse Gas Emissions Data (2018)."
  )
}

fig_ch1_GHG_emissions_pie()

figure_save_draft_png(fig_ch1_GHG_emissions_pie(), style_SAR_CCDR, "../png/fig_ch1_GHG_emissions_pie.png", height=5.1, width=5.5)
```




&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Vulnerability score

Data source: https://gain.nd.edu/our-work/country-index/download-data/

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=4.1, out.width=800, dpi=200}
library(ggradar)
library(showtext)

fig_ch1_vulnerability <- function() {
  
  # data
  df <- read_csv("../data/vulnerability.csv")

  # add regions and income levels
  df <- df %>%
    rename(iso3c = ISO3) %>%
    left_join(wbgref$countries$regions, by="iso3c") %>%
    left_join(wbgref$countries$incomegroups, by="iso3c")
  
  # calculate aggregates by regions
  region_aggregates <- df %>%
    group_by(region_iso3c) %>% summarize(ecosystems = mean(ecosystems, na.rm=TRUE),
                                         food = mean(food, na.rm=TRUE),
                                         health = mean(health, na.rm=TRUE),
                                         habitat = mean(habitat, na.rm=TRUE),
                                         infrastructure = mean(infrastructure, na.rm=TRUE),
                                         water = mean(water, na.rm=TRUE)) %>%
    rename(iso3c = region_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$regions$labels), Name = wbgref$regions$labels), by="iso3c")
    
  # calculate aggregates by income levels
  income_level_aggregates <- df %>%
    group_by(income_level_iso3c) %>% summarize(ecosystems = mean(ecosystems, na.rm=TRUE),
                                         food = mean(food, na.rm=TRUE),
                                         health = mean(health, na.rm=TRUE),
                                         habitat = mean(habitat, na.rm=TRUE),
                                         infrastructure = mean(infrastructure, na.rm=TRUE),
                                         water = mean(water, na.rm=TRUE)) %>%
    rename(iso3c = income_level_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$incomes$labels), Name = wbgref$incomes$labels), by="iso3c")
  
  # merge and select
  df <- df %>%
    bind_rows(region_aggregates, income_level_aggregates) %>%
    filter(iso3c == "BGD" | iso3c == "LMC" | iso3c == "SAS") %>%
    select(Name, ecosystems, food, health, habitat, infrastructure, water)
  
  # rescale
  min <- 0.3
  max <- 0.9
  min_max_norm <- function(x) {
    (x - min) / (max - min)
  }
  df <- df %>%
    mutate(ecosystems = min_max_norm(ecosystems)) %>%
    mutate(food = min_max_norm(food)) %>%
    mutate(health = min_max_norm(health)) %>%
    mutate(habitat = min_max_norm(habitat)) %>%
    mutate(infrastructure = min_max_norm(infrastructure)) %>%
    mutate(water = min_max_norm(water))
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggradar(
        df,
        background.circle.colour = "white",
        font.radar = style$family,
        values.radar = c(min, (min+max)/2, max),
        grid.min = 0, grid.mid = 0.5, grid.max = 1,
        grid.label.size = 3,  # Affects the grid annotations (0%, 50%, etc.)
        axis.label.size = 3, # Afftects the names of the variables
        group.point.size = 3   # Simply the size of the point 
      ) +
      style$theme() +
      theme(
        line = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        legend.position = c(1, 0),  
        legend.justification = c(1, 0),
        legend.text = element_text(size = 7, family = style$family),
        legend.key = element_rect(fill = NA, color = NA),
        legend.background = element_blank()
      ) +
      scale_color_manual(values = c(
        "Lower middle income" = style$colors$spot.secondary, 
        "South Asia" = style$colors$spot.secondary.light,
        "Bangladesh" = style$colors$spot.primary
      ))
    },
    aspect_ratio = 1,
    title = "Bangladesh's vulnerability in six life-supporting sectors.",
    subtitle = "Vulnerability scores (0-1 lower is better), 2019",
    note = "Note: Vulnerability measures a country's exposure, sensitivity and ability to adapt to the negative impact of climate change.",
    source = "Source: The Notre Dame-Global Adaptation Index (ND-GAIN) Country Index."
  )
}

fig_ch1_vulnerability()

figure_save_draft_png(fig_ch1_vulnerability(), style_SAR_CCDR, "../png/fig_ch1_vulnerability.png", height=4.1, width=4.1)
```



&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Readiness score

Data source: https://gain.nd.edu/our-work/country-index/download-data/

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=4.1, out.width=800, dpi=200}
library(ggradar)
library(showtext)

fig_ch1_readiness <- function() {
  
  # data
  df <- read_csv("../data/readiness.csv")

  # add regions and income levels
  df <- df %>%
    rename(iso3c = ISO3) %>%
    left_join(wbgref$countries$regions, by="iso3c") %>%
    left_join(wbgref$countries$incomegroups, by="iso3c")
  
  # calculate aggregates by regions
  region_aggregates <- df %>%
    group_by(region_iso3c) %>% summarize(economic = mean(economic, na.rm=TRUE),
                                         governance = mean(governance, na.rm=TRUE),
                                         social = mean(social, na.rm=TRUE)) %>%
    rename(iso3c = region_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$regions$labels), Name = wbgref$regions$labels), by="iso3c")
    
  # calculate aggregates by income levels
  income_level_aggregates <- df %>%
    group_by(income_level_iso3c) %>% summarize(economic = mean(economic, na.rm=TRUE),
                                         governance = mean(governance, na.rm=TRUE),
                                         social = mean(social, na.rm=TRUE)) %>%
    rename(iso3c = income_level_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$incomes$labels), Name = wbgref$incomes$labels), by="iso3c")
  
  # merge and select
  df <- df %>%
    bind_rows(region_aggregates, income_level_aggregates) %>%
    filter(iso3c == "BGD" | iso3c == "LMC" | iso3c == "SAS") %>%
    select(Name, economic, governance, social)
  
  # rescale
  min <- 0.2
  max <- 0.45
  min_max_norm <- function(x) {
    (x - min) / (max - min)
  }
  df <- df %>%
    mutate(economic = min_max_norm(economic)) %>%
    mutate(governance = min_max_norm(governance)) %>%
    mutate(social = min_max_norm(social))
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggradar(
        df,
        background.circle.colour = "white",
        font.radar = style$family,
        values.radar = c(min, (min+max)/2, max),
        grid.min = 0, grid.mid = 0.5, grid.max = 1,
        grid.label.size = 3,  # Affects the grid annotations (0%, 50%, etc.)
        axis.label.size = 3, # Afftects the names of the variables
        group.point.size = 3   # Simply the size of the point 
      ) +
      style$theme() +
      theme(
        line = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        legend.position = c(1, 0),  
        legend.justification = c(1, 0),
        legend.text = element_text(size = 7, family = style$family),
        legend.key = element_rect(fill = NA, color = NA),
        legend.background = element_blank()
      ) +
      scale_color_manual(values = c(
        "Lower middle income" = style$colors$spot.secondary, 
        "South Asia" = style$colors$spot.secondary.light,
        "Bangladesh" = style$colors$spot.primary
      ))
    },
    aspect_ratio = 1,
    title = "Bangladesh's readiness in economic opportunity, governance, and social structures.",
    subtitle = "Readiness scores (0-1 higher is better), 2019",
    note = "Note: Readiness measures a country’s ability to leverage investments and convert them to adaptation actions.",
    source = "Source: The Notre Dame-Global Adaptation Index (ND-GAIN) Country Index."
  )
}

fig_ch1_readiness()

figure_save_draft_png(fig_ch1_readiness(), style_SAR_CCDR, "../png/fig_ch1_readiness.png", height=4.1, width=4.1)

```






```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=8.2, out.width=800, dpi=200}

library(zoo)

fig_ch1_vulnerability_readiness <- function() {

  # vulnerability data
  df <- read_csv("../data/vulnerability.csv")

  # add regions and income levels
  df <- df %>%
    rename(iso3c = ISO3) %>%
    left_join(wbgref$countries$regions, by="iso3c") %>%
    left_join(wbgref$countries$incomegroups, by="iso3c")
  
  # calculate aggregates by regions
  region_aggregates <- df %>%
    group_by(region_iso3c) %>% summarize(ecosystems = mean(ecosystems, na.rm=TRUE),
                                         food = mean(food, na.rm=TRUE),
                                         health = mean(health, na.rm=TRUE),
                                         habitat = mean(habitat, na.rm=TRUE),
                                         infrastructure = mean(infrastructure, na.rm=TRUE),
                                         water = mean(water, na.rm=TRUE)) %>%
    rename(iso3c = region_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$regions$labels), Name = wbgref$regions$labels), by="iso3c")
    
  # calculate aggregates by income levels
  income_level_aggregates <- df %>%
    group_by(income_level_iso3c) %>% summarize(ecosystems = mean(ecosystems, na.rm=TRUE),
                                         food = mean(food, na.rm=TRUE),
                                         health = mean(health, na.rm=TRUE),
                                         habitat = mean(habitat, na.rm=TRUE),
                                         infrastructure = mean(infrastructure, na.rm=TRUE),
                                         water = mean(water, na.rm=TRUE)) %>%
    rename(iso3c = income_level_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$incomes$labels), Name = wbgref$incomes$labels), by="iso3c")
  
  # merge and select
  df <- df %>%
    bind_rows(region_aggregates, income_level_aggregates) %>%
    filter(iso3c == "BGD" | iso3c == "LMC" | iso3c == "SAS") %>%
    select(Name, ecosystems, food, health, habitat, infrastructure, water)
  
  # rescale
  vulnerability.min <- 0.3
  vulnerability.max <- 0.9
  vulnerability.min_max_norm <- function(x) {
    (x - vulnerability.min) / (vulnerability.max - vulnerability.min)
  }
  df.vulnerability <- df %>%
    mutate(ecosystems = vulnerability.min_max_norm(ecosystems)) %>%
    mutate(food = vulnerability.min_max_norm(food)) %>%
    mutate(health = vulnerability.min_max_norm(health)) %>%
    mutate(habitat = vulnerability.min_max_norm(habitat)) %>%
    mutate(infrastructure = vulnerability.min_max_norm(infrastructure)) %>%
    mutate(water = vulnerability.min_max_norm(water))
  
  # readiness data
  df <- read_csv("../data/readiness.csv")

  # add regions and income levels
  df <- df %>%
    rename(iso3c = ISO3) %>%
    left_join(wbgref$countries$regions, by="iso3c") %>%
    left_join(wbgref$countries$incomegroups, by="iso3c")
  
  # calculate aggregates by regions
  region_aggregates <- df %>%
    group_by(region_iso3c) %>% summarize(economic = mean(economic, na.rm=TRUE),
                                         governance = mean(governance, na.rm=TRUE),
                                         social = mean(social, na.rm=TRUE)) %>%
    rename(iso3c = region_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$regions$labels), Name = wbgref$regions$labels), by="iso3c")
    
  # calculate aggregates by income levels
  income_level_aggregates <- df %>%
    group_by(income_level_iso3c) %>% summarize(economic = mean(economic, na.rm=TRUE),
                                         governance = mean(governance, na.rm=TRUE),
                                         social = mean(social, na.rm=TRUE)) %>%
    rename(iso3c = income_level_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$incomes$labels), Name = wbgref$incomes$labels), by="iso3c")
  
  # merge and select
  df <- df %>%
    bind_rows(region_aggregates, income_level_aggregates) %>%
    filter(iso3c == "BGD" | iso3c == "LMC" | iso3c == "SAS") %>%
    select(Name, economic, governance, social)
  
  # rescale
  readiness.min <- 0.2
  readiness.max <- 0.5
  readiness.min_max_norm <- function(x) {
    (x - readiness.min) / (readiness.max - readiness.min)
  }
  df.readiness <- df %>%
    mutate(economic = readiness.min_max_norm(economic)) %>%
    mutate(governance = readiness.min_max_norm(governance)) %>%
    mutate(social = readiness.min_max_norm(social))
  
  df <- merge(x = df.vulnerability, y = df.readiness, by = "Name", all = TRUE)
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      
      df.vulnerability <- df %>%
        select(Name, ecosystems, food, health, habitat, infrastructure, water)
      
      p.vulnerability <- ggradar(
          df.vulnerability,
          background.circle.colour = "white",
          font.radar = style$family,
          values.radar = c(vulnerability.min, (vulnerability.min+vulnerability.max)/2, vulnerability.max),
          grid.min = 0, grid.mid = 0.5, grid.max = 1,
          grid.label.size = 3,  # Affects the grid annotations (0%, 50%, etc.)
          axis.label.size = 3, # Afftects the names of the variables
          group.point.size = 3   # Simply the size of the point 
        ) +
        style$theme() +
        theme(
          plot.subtitle=element_text(hjust=0.5),
          line = element_blank(),
          axis.text.y = element_blank(),
          axis.text.x = element_blank(),
          legend.position = c(1, 0),  
          legend.justification = c(1, 0),
          legend.text = element_text(size = 7, family = style$family),
          legend.key = element_rect(fill = NA, color = NA),
          legend.background = element_blank()
        ) +
        scale_color_manual(values = c(
          "Lower middle income" = style$colors$spot.secondary, 
          "South Asia" = style$colors$spot.secondary.light,
          "Bangladesh" = style$colors$spot.primary
        )) +
        labs(subtitle = "Vulnerability scores (0-1 lower is better), 2019")
      
      df.readiness <- df %>%
        select(Name, economic, governance, social)
      
      p.readiness <- ggradar(
          df.readiness,
          background.circle.colour = "white",
          font.radar = style$family,
          values.radar = c(readiness.min, (readiness.min+readiness.max)/2, readiness.max),
          grid.min = 0, grid.mid = 0.5, grid.max = 1,
          grid.label.size = 3,  # Affects the grid annotations (0%, 50%, etc.)
          axis.label.size = 3, # Afftects the names of the variables
          group.point.size = 3   # Simply the size of the point 
        ) +
        style$theme() +
        theme(
          plot.subtitle=element_text(hjust=0.5),
          line = element_blank(),
          axis.text.y = element_blank(),
          axis.text.x = element_blank(),
          legend.position = c(1, 0),  
          legend.justification = c(1, 0),
          legend.text = element_text(size = 7, family = style$family),
          legend.key = element_rect(fill = NA, color = NA),
          legend.background = element_blank()
        ) +
        scale_color_manual(values = c(
          "Lower middle income" = style$colors$spot.secondary, 
          "South Asia" = style$colors$spot.secondary.light,
          "Bangladesh" = style$colors$spot.primary
        )) +
        labs(subtitle = "Readiness scores (0-1 higher is better), 2019")
      
      
      pt.vulnerability <- ggplotGrob(p.vulnerability)
      pt.readiness <- ggplotGrob(p.readiness)
  
      chart <- gtable_row(
        "chart", 
        list(pt.vulnerability, zeroGrob(), pt.readiness), 
        height = unit(1, "null"), 
        widths = unit.c(unit(1, "null"), unit(0.3, "in"), unit(1, "null"))
        )
      chart$theme <- style$theme()
      chart
      
    },
    aspect_ratio = 1,
    title = "Bangladesh's climate vulnerability and adaptation readiness",
    note = "Note: Vulnerability measures a country's exposure, sensitivity and ability to adapt to the negative impact of climate change while Readiness measures a country’s ability to leverage investments and convert them to adaptation actions.",
    source = "Source: The Notre Dame-Global Adaptation Index (ND-GAIN) Country Index."
  )
}

fig_ch1_vulnerability_readiness()

figure_save_draft_png(fig_ch1_vulnerability_readiness(), style_SAR_CCDR, "../png/fig_ch1_vulnerability_readiness.png", height=4.1, width=8.2)

```



&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## ND-GAIN

Data source: https://gain.nd.edu/our-work/country-index/download-data/

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=3.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_nd_gain <- function() {
  
  # data
  df <- read_csv("../data/ND-gain.csv")

  # add regions and income levels
  df <- df %>%
    rename(iso3c = ISO3) %>%
    left_join(wbgref$countries$regions, by="iso3c") %>%
    left_join(wbgref$countries$incomegroups, by="iso3c")

  # calculate aggregates by regions
  region_aggregates <- df %>%
    group_by(region_iso3c) %>% summarise(across(where(is.double), ~ mean(.x, na.rm = TRUE))) %>%
    rename(iso3c = region_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$regions$labels), Name = wbgref$regions$labels), by="iso3c")
  
  # calculate aggregates by income levels
  income_level_aggregates <- df %>%
    group_by(income_level_iso3c) %>% summarise(across(where(is.double), ~ mean(.x, na.rm = TRUE))) %>%
    rename(iso3c = income_level_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$incomes$labels), Name = wbgref$incomes$labels), by="iso3c")
  
  # merge and select
  df <- df %>%
    bind_rows(region_aggregates, income_level_aggregates) %>%
    filter(iso3c == "BGD" | iso3c == "LMC" | iso3c == "SAS") %>%
    select(-c(region_iso3c, income_level_iso3c)) %>%
    gather(key="Year", value="Gain", "1995":"2019") %>%
    select(iso3c, Name, Year, Gain) %>%
    mutate(Year = as.numeric(Year))
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      ggplot(df, aes(x = Year, y = Gain, group = rev(iso3c), color = iso3c)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$Year), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df %>% filter(Year == max(Year)) %>% pull(Gain) %>% repel(gap=6),
            labels = df %>% filter(Year == max(Year)) %>% pull(Name)
          )) +
        scale_color_manual(values = c(
          "LMC" = style$colors$spot.secondary.light, 
          "SAS" = style$colors$spot.secondary.light,
          "BGD" = style$colors$spot.primary)) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Bangladesh's ND-GAIN dropped by nearly 10% points in 2014.",
    subtitle = "ND-GAIN Country Index (0-100 higher is better), 1995-2019",
    note = "Note: The ND-GAIN Country Index summarizes a country's vulnerability to climate change and other global challenges in combination with its readiness to improve resilience.",
    source = "Source: The Notre Dame-Global Adaptation Index (ND-GAIN) Country Index."
  )
}

fig_ch1_nd_gain()

figure_save_draft_png(fig_ch1_nd_gain(), style_SAR_CCDR, "../png/fig_ch1_nd_gain.png", height=3.1, width=5.5)
```







