---
title: "Pakistan CCDR - 00. Visuzlization Examples"
date: "2/16/2022"
output:
  html_document: default
---

This R Makrdown notebook outlines visualizations/data sources for Pakistan Country Climate and Development Report (CCDR). We use several R packages and customized style functions that are modified from [bbplot](https://github.com/bbc/bbplot) and [SDG Atlas 2018](https://github.com/worldbank/sdgatlas2018) to produce publication-ready graphics for the CCDR.

### Required packages and settings

```{r, results='hide', message=FALSE}
source("../styles/CCDR_basic_style.R")
source("../styles/SDG_atlas_styles.R")
source("../utils/CCDR_utils.R")
library(knitr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggalt)
library(forcats)
library(png)
library(ggpubr)
library(scales)
library(hrbrthemes)
library(viridis)
library(wbstats)
library(wbgcharts)
library(wbgmaps)
library(wbggeo)
library(readr)
library(readxl)
library(gtable)
library(grid)
library(lubridate)
library(extrafont)
# this only needs to be done once
# library(remotes)
# remotes::install_version("Rttf2pt1", version = "1.3.8")
# font_import() 
# loadfonts(device = 'win')
create_wbgref()
```


### Chart example 1

```{r fig.height=8, fig.width=10, fig.align = "center"}
# The dataset is provided in the gapminder library
library(gapminder)
data <- gapminder %>% filter(year=="2007") %>% dplyr::select(-year)

# Most basic bubble plot
data %>%
  arrange(desc(pop)) %>%
  mutate(country = factor(country, country)) %>%
  ggplot(aes(x=gdpPercap, y=lifeExp, size=pop, color=continent, fill=continent)) +
    geom_point(alpha=0.5, shape=21, color="black") +
    scale_size(range = c(.1, 24), name="Population (M)", 
               breaks = 1000000 * c(250, 500, 750, 1000, 1250),
               labels = c("250", "500", "750", "1000", "1250")) +
    scale_fill_viridis(name="Continent", discrete=TRUE, option="A", guide=guide_legend(override.aes=list(size=5))) +
    theme_ipsum() +
    theme(legend.position="right") +
    theme(axis.title.y=element_text(size=12)) +
    theme(axis.title.x=element_text(size=12)) +
    ylab("Life Expectancy") +
    xlab("GDP per Capita") +
    labs(title="Logarithmic trend between GDP and live expectancy across countries.",
         subtitle="GDP versus life expectancy, 2007")
```


### Chart example 2

```{r, message=FALSE, warning = FALSE, fig.height=5, fig.width=7, out.width=400, dpi=200}
#Prepare data
library(gapminder)
dumbbell_df <- gapminder %>%
  filter(country == "India" | country == "Bangladesh" | country == "Nepal" | country == "Pakistan") %>%
  filter(year == 1967 | year == 2007) %>%
  select(country, year, lifeExp) %>%
  spread(year, lifeExp) %>%
  mutate(gap = `2007` - `1967`) %>%
  arrange(desc(gap))

#Make plot
ggplot(dumbbell_df, aes(x = `1967`, xend = `2007`, y = reorder(country, gap), group = country)) + 
  geom_dumbbell(colour = "#dddddd",
                size = 3,
                colour_x = "#FAAB18",
                colour_xend = "#1380A1") +
  CCDR_basic_style() +
  labs(title="We're living longer",
       subtitle="Biggest life expectancy rise, 1967-2007")
```


### Chart example 3

```{r, message=FALSE, warning = FALSE, fig.height=2.4, fig.width=2.94, out.width=400, dpi=200}
# data
chart_example_3 <- function() {
  df <- read_table(
      "../data/co2_mm_mlo.txt",
      col_names = c("year", "month", "decimal_date", "average", "interpolated", "trend", "num_days"),
      comment = "#",
      na = c("-99.99", "-1")
    )
    
  df <- df %>% mutate(date = date_decimal(decimal_date))
  
  # chart
  figure(
      data = df,
      plot = function(df, style = style_atlas()) {
        ggplot(df, aes(x = decimal_date)) +
          geom_line(aes(y = average), color = style$colors$spot.primary, size = style$linesize) +
          geom_line(aes(y = trend), color = style$colors$spot.secondary, size = style$linesize) +
          scale_x_continuous(limits = c(1960, 2018), breaks = c(1960, 1980, 2000, 2017)) +
          scale_y_continuous(breaks = seq(320,400,20), position = "left") +
          style$theme()
      },
      aspect_ratio = 1,
      title = "...so its concentration in the atmosphere is also growing—at an accelerating rate.",
      subtitle = "Atmospheric CO2 at Mauna Loa, Hawaii, parts per million",    
      source = "Source: Tans, P / NOAA/ESRL & Keeling, R / Scripps Institution of Oceanography. http://www.esrl.noaa.gov/gmd/ccgg/trends"
    )
}
chart_example_3()
```


### Chart example 4

```{r, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=5.5, out.width=800, dpi=200}
# data
year <- 2016
df <- read_xlsx("../data/NDC readiness vulnerability data.xlsx", sheet="NDC readiness", .name_repair = "minimal")

iso3c_to_income_mapping <- setNames(wbgref$countries$incomegroups$income_level_iso3c, wbgref$countries$incomegroups$iso3c)
df <- df %>% 
  select(iso3c = "ISO3",
         readiness = "Readiness 2016",
         vulnerability = "Vulnerability 2016"
  ) %>% 
  mutate(income_group = iso3c_to_income_mapping[iso3c])

# plot
figure(
  data = df,
  plot = function(df, style = style_atlas()) {
    ggplot(df, aes(x = readiness, y = vulnerability, color = factor(income_group, levels = c("LIC", "LMC", "UMC", "HIC")))) +
      geom_point(size = style$point_size, stroke = style$point_stroke, shape = style$shapes$point, alpha = 0.8) +
      scale_color_manual(values = style$colors$incomes, labels = wbgref$incomes$labels) +
      scale_x_continuous(limits = c(0,0.8)) +
      scale_y_continuous(limits = c(0.2,0.8)) +
      coord_equal() +
      labs(x = wbg_name(indicator = "Readiness to make effective use of investments for adaptation actions, score\n", denom = "0–1, higher is more ready")) +
      style$theme() +
      style$theme_scatter() +
      style$theme_legend("righttop")
  },
  aspect_ratio = 1.3,
  title = "Low-income countries tend to be more vulnerable to, and less equipped to invest against, extreme climate impacts.",
  subtitle = wbg_name(indicator = "Vulnerability to climate hazards, score", by = "by country", year = year, denom = "0–1, higher is more vulnerable"),
  source = "Source: Notre Dame Global Adaptation Initiative Country Index (database). https://gain.nd.edu/our-work/country-index"
)
```


### Chart example 5

```{r, message=FALSE, warning = FALSE, fig.height=3.5, fig.width=5.5, out.width=800, dpi=200}
# data
df <- wb_data(
  indicator = c("EN.ATM.CO2E.KT"),
  country = c(wbgref$regions$iso3c),
  start_date = 1960,
  end_date = 2021
)
df <- df %>% 
  mutate(num_def = EN.ATM.CO2E.KT) %>% 
  select(iso3c, date, num_def) %>% 
  spread(iso3c, num_def) %>% 
  gather(iso3c, num_def, EAS:SSF)
  

# plot
figure(
  data = df,
  plot = function(data, style = style_atlas_open()) {
    region_levels <- data[which(data$date == max(2018)), ] %>%
      pull(iso3c)
    
    ggplot(data, aes(x = date, y = num_def, fill = factor(iso3c, levels = region_levels))) +
      geom_area() +
      style$theme() + 
      style$theme_legend("right") +
      scale_x_continuous(expand = c(0, 0)) +
      scale_y_continuous(labels = millions()) +
      scale_fill_manual(
        values = c(style$colors$regions),
        labels = c(wbgref$regions$labels)
      )
    },
    aspect_ratio = 1.5,
    title = paste0("Carbon dioxide (CO2) emissions have been growing globally."),
    subtitle = "Annual CO2 emissions (Gt)",
    source = "Source: Carbon Dioxide Information Analysis Center. World Development Indicators (EN.ATM.CO2E.KT)."
)
```


### Chart example 6

```{r, message=FALSE, warning = FALSE, fig.height=3.5, fig.width=5.5, out.width=800, dpi=200}
# data
df <- wb_data(
  indicator = c("EN.ATM.CO2E.KT"),
  country = wbgref$countries$regions %>% filter(region_iso3c == "SAS") %>% select(iso3c) %>% unlist(),
  start_date = 1960,
  end_date = 2021
)
df <- df %>% 
  mutate(num_def = EN.ATM.CO2E.KT) %>% 
  select(iso3c, date, num_def) %>% 
  spread(iso3c, num_def) %>% 
  gather(iso3c, num_def, AFG:PAK)
  

# plot
figure(
  data = df,
  plot = function(data, style = style_atlas()) {
    country_levels <- data[which(data$date == max(2018)), ] %>%
      pull(iso3c)
    
    ggplot(data, aes(x = date, y = num_def, fill = factor(iso3c, levels = country_levels))) +
      geom_area() +
      style$theme() + 
      style$theme_legend("right") +
      scale_x_continuous(expand = c(0, 0)) +
      scale_y_continuous(labels = millions()) +
      scale_fill_manual(
        values = c("AFG" = unname(style$colors$regions.light["EAS"]), 
                   "BGD" = unname(style$colors$regions.light["ECS"]),  
                   "BTN" = unname(style$colors$regions.light["LCN"]),  
                   "IND" = unname(style$colors$regions.light["SAS"]),  
                   "LKA" = unname(style$colors$regions.light["NAC"]),  
                   "MDV" = unname(style$colors$regions.light["MEA"]),  
                   "NPL" = unname(style$colors$regions.light["SSF"]),  
                   "PAK" = unname(style$colors$spot.primary)),
        labels = c(wbgref$countries$labels)
      )
    },
    aspect_ratio = 1.5,
    title = paste0("Carbon dioxide (CO2) emissions are growing exponentially in the South Asia region."),
    subtitle = "Annual CO2 emissions (Gt)",
    source = "Source: Carbon Dioxide Information Analysis Center. World Development Indicators (EN.ATM.CO2E.KT)."
)
```


### Chart example 7

```{r, message=FALSE, warning = FALSE,  fig.height=4, fig.width=10, out.width=1000, dpi=200}
# data
df <- wb_data(
  indicator = c("EN.ATM.CO2E.KT"),
  country = c(wbgref$regions$iso3c, wbgref$countries$regions %>% filter(region_iso3c == "SAS") %>% select(iso3c) %>% unlist()),
  start_date = 1960,
  end_date = 2021
)

figure(
  data = df, 
  plot = function(data, style = style_atlas()) {
    
    df_region <- data %>% 
    filter(iso3c %in% wbgref$regions$iso3c) %>%
    mutate(num_def = EN.ATM.CO2E.KT) %>% 
    select(iso3c, date, num_def) %>% 
    spread(iso3c, num_def) %>% 
    gather(iso3c, num_def, EAS:SSF)
    region_levels <- df_region[which(df_region$date == max(2018)), ] %>% pull(iso3c)

    p.region <- ggplot(df_region, aes(x = date, y = num_def, fill = factor(iso3c, levels = region_levels))) +
      geom_area() +
      style$theme() + 
      style$theme_legend("top") +
      scale_x_continuous(expand = c(0, 0)) +
      scale_y_continuous(labels = millions()) +
      scale_fill_manual(
        values = c("EAS" = "#646E78", 
                   "ECS" = "#8D98A7",   
                   "LCN" = "#B5B2B1",   
                   "MEA" = "#DCCCBB",   
                   "NAC" = "#EAB464",   
                   "SAS" = "#931621",  
                   "SSF" = "#A7754D"), 
        labels = c(wbgref$regions$labels)
      ) 
    
    df_SAS <- data %>% 
    filter(!iso3c %in% wbgref$regions$iso3c) %>%
    mutate(num_def = EN.ATM.CO2E.KT) %>% 
    select(iso3c, date, num_def) %>% 
    spread(iso3c, num_def) %>% 
    gather(iso3c, num_def, AFG:PAK)
    country_levels <- df_SAS[which(df_SAS$date == max(2018)), ] %>% pull(iso3c)
    
    p.SAS <- ggplot(df_SAS, aes(x = date, y = num_def, fill = factor(iso3c, levels = country_levels))) +
      geom_area() +
      style$theme() + 
      style$theme_legend("top") +
      scale_x_continuous(expand = c(0, 0)) +
      scale_y_continuous(labels = millions()) +
      scale_fill_manual(
        values = c("AFG" = "#42D9C8", 
                   "BGD" = "#3DC6BD",   
                   "BTN" = "#37B3B1",   
                   "IND" = "#2C8C99",   
                   "LKA" = "#326771",   
                   "MDV" = "#2D575E",  
                   "NPL" = "#28464B",   
                   "PAK" = "#931621"), 
        labels = c(wbgref$countries$labels)
      )

    pt.region <- ggplotGrob(p.region)
    pt.SAS <- ggplotGrob(p.SAS)

    chart <- gtable_row(
      "chart", 
      list(pt.region, zeroGrob(), pt.SAS), 
      height = unit(1, "null"), 
      widths = unit.c(unit(1, "null"), unit(0.25, "in"), unit(1, "null"))
      )
    chart$theme <- style$theme()
    chart
  },
  aspect_ratio = 1,
  title = paste0("Carbon dioxide (CO2) emissions have been growing globally with a notable exponential increase in the South Asia region."),
  subtitle = "Annual CO2 emissions (Gt)",
  source = "Source: Carbon Dioxide Information Analysis Center. World Development Indicators (EN.ATM.CO2E.KT)."
)
```


