---
title: "Pakistan CCDR - 01. Climate and Development"
date: "03/11/2022"
output:
  github_document: default
  html_document: default
knit: (function(inputFile, encoding) {
      out_dir <- "../html/";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_format = "all",
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

This chapter will place Pakistan’s core development priorities and challenges in the context of climate change.  and assess the immediate and longer-term risks to sustainable and inclusive development from climate change. The assessment of Pakistan’s core development priorities will be placed in the context of the government’s development vision and revised NDCs, the draft World Bank’s Country Partnership Framework (CPF) and the Country Climate Action Plan (CCAP) for Pakistan. It will summarize the main sectoral, macro-fiscal and financial opportunities to address critical development needs while building climate resilience and reducing emissions, with a focus on synergistic short- and medium-term strategies that are urgent for sustainable and inclusive growth and poverty reduction while transitioning to a resilient and low carbon economy.

### Required packages and settings

```{r, results='hide', message=FALSE}
source("../../styles/CCDR_basic_style.R")
source("../../styles/SDG_atlas_styles.R")
source("../../utils/CCDR_utils.R")
library(knitr)
library(dplyr)
library(tidyr)
library(tidyverse)
library(stringr)
library(ggplot2)
library(ggalt)
library(forcats)
library(png)
library(ggpubr)
library(ggrepel)
library(scales)
library(hrbrthemes)
library(viridis)
library(wbstats)
library(wbgcharts)
library(wbgmaps)
library(wbggeo)
library(readr)
library(readxl)
library(gtable)
library(grid)
library(lubridate)
library(extrafont)
# this only needs to be done once
# library(remotes)
# remotes::install_version("Rttf2pt1", version = "1.3.8")
# font_import() 
# loadfonts(device = 'win')
create_wbgref()
```


## 1.1	Economic, Social and Environmental Contexts

```{r, message=FALSE, warning = FALSE, fig.height=3.1, fig.width=5.5, out.width=800, dpi=200}
fig_ch1_economic_growth <- function() {

  # data
  df <- wb_data(
    indicator = c("NY.GDP.PCAP.PP.CD"),
    country = c("PAK", "LMC", "SAS"),
    start_date = 1990,
    end_date = 2020
  )
  df <- df %>% 
    mutate(num_def = NY.GDP.PCAP.PP.CD) %>% 
    select(iso3c, country, date, num_def) 
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_atlas()) {
      ggplot(df, aes(x = date, y = num_def, group = rev(iso3c), color = iso3c)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$date), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df %>% filter(date == max(date)) %>% pull(num_def) %>% repel(gap=6),
            labels = df %>% filter(date == max(date)) %>% pull(country)
          )) +
        scale_color_manual(values = c(
          "XN" = "#888D8E", 
          "SAS" = "#7F7B7A",
          "PAK" = "#8C271E")) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Pakistan's economic growth compared with South Asia and lower-middle-income group",
    subtitle = "GDP per capita, PPP (current international $), 1990 to 2020",
    source = "Source: World Development Indicators (NY.GDP.PCAP.PP.CD)."
  )
}

fig_ch1_economic_growth()

figure_save_draft_png(fig_ch1_economic_growth(), style_atlas, "../drafts/fig_ch1_economic_growth.png", height=3.1, width=5.5)

```


```{r, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=6.5, out.width=800, dpi=200}
fig_ch1_TES_share_by_source <- function() {
  
  # data
  df <- read_csv("../data/Total energy supply (TES) by source - Pakistan.csv", skip=4) %>%
    rename(year = X1) %>%
    select(-Units)
  df <- df %>%
    gather(source, TJ, 2:8) %>%
    group_by(year) %>%
    mutate(percentage =  100 *TJ/sum(TJ, na.rm=TRUE)) %>%
    mutate(year = as.numeric(year))
  
  # plot
  color_list <- c("#45462A", "#227C9D", "#443850", "#BCAA99", "#3AAFB9", "#8E5572", "#BBBE64")
  figure(
    data = df,
    plot = function(data, style = style_atlas_open()) {
      ggplot(df, aes(x = year, y = percentage, fill = source)) +
        geom_area() +
        style$theme() + 
        style$theme_legend("right") +
        scale_x_continuous(expand = c(0, 1)) +
        # scale_y_continuous(labels = millions()) +
        scale_fill_manual(values=color_list)
      },
      aspect_ratio = 1.5,
      title = paste0("Pakistan's total energy supply (TES)"),
      subtitle = "Share by source (%), 1990-2019",
      note = "Note: TES is made up of production + imports - exports - international marine bunkers - international aviation bunkers ± stock changes.",
      source = "Source: IEA World Energy Balances https://www.iea.org/data-and-statistics/data-product/world-energy-statistics-and-balances"
  )
}

fig_ch1_TES_share_by_source()

figure_save_draft_png(fig_ch1_TES_share_by_source(), style_atlas, "../drafts/fig_ch1_TES_share_by_source.png", height=4.1, width=6.5)

```




## 1.2	Climate Risks Pertinent to Sustainable and Inclusive Development 

```{r, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=5.5, out.width=800, dpi=200}
fig_ch1_natural_disasters <- function() {
  
  # data
  df1 <- read_csv("../data/natural-disasters_pakistan_deaths.csv")
  names(df1) <- c('Entity', 'Code', 'Year', 'Extreme temperature', 'Wildfires', 'Storms', 
                  'Landslides', 'Mass movement (dry)', 'Volcanic activity', 'Earthquakes', 'Floods', 'Drought')
  df1 <- df1 %>%
    select(-c('Wildfires', 'Mass movement (dry)', 'Volcanic activity')) %>%
    gather(Type, Deaths, 4:9) %>%
    select(Year, Type, Deaths)
  
  df2 <- read_csv("../data/natural-disasters_pakistan_gdp.csv")
  names(df2) <- c('Entity', 'Code', 'Year', 'Extreme temperature', 'Wildfires', 'Storms', 
                  'Landslides', 'Mass movement (dry)', 'Volcanic activity', 'Earthquakes', 'Floods', 'Drought')
  df2 <- df2 %>%
    select(-c('Wildfires', 'Mass movement (dry)', 'Volcanic activity')) %>%
    gather(Type, Damage, 4:9) %>%
    mutate(Damage = Damage*100) %>%
    select(Year, Type, Damage)
  
  df <- merge(df1, df2, by=c("Year", "Type"))
  
  # chart
  figure(
    data =  df,
    plot = function(df, style = style_atlas()) {
      p <- ggplot(df, aes(x=Year, y=reorder(Type, desc(Type)), size=ifelse(Damage==0, NA, Damage), color=Deaths, fill=Deaths)) +
        geom_point(alpha=0.5, shape=21, color="black") +
        scale_size(range = c(1, 20), name="Damage (%GDP)",
                   breaks = c(10, 50,100),
                   labels = c("10", "50", "100")) +
        scale_fill_distiller(direction=1) + 
        scale_x_continuous(limits = c(1960, 2012)) +
        xlab("Year") +
        ylab("Natural Disasters") +
        geom_curve(aes(x = 1990, y = 4.5, xend = 1997, yend = 5), 
                               colour = "#555555", 
                               size=0.3, 
                               curvature = -0.2,
                               arrow = arrow(length = unit(0.03, "npc"))) +
        annotate("text", x = 1990, y = 4.3, label = "including 2005 Kashmir earthquake", size = 2.5, family = style$family) +
        geom_curve(aes(x = 1975, y = 1.5, xend = 1974, yend = 2.6), 
                               colour = "#555555", 
                               size=0.3, 
                               curvature = 0.2,
                               arrow = arrow(length = unit(0.03, "npc"))) +
        annotate("text", x = 1975, y = 1.4, label = "including 1970 East Pakistan cyclone", size = 2.5, family = style$family) +
        geom_curve(aes(x = 2000, y = 2, xend = 2006, yend = 2.7), 
                               colour = "#555555", 
                               size=0.3, 
                               curvature = -0.2,
                               arrow = arrow(length = unit(0.03, "npc"))) +
        annotate("text", x = 2000, y = 1.9, label = "including 2010 floods", size = 2.5, family = style$family) +
        style$theme() +
        theme(
          axis.title.x = element_text(vjust = -5),
          axis.title.y = element_text(angle = 90, vjust = 0, margin = margin(r = 15)),
          axis.text.x = element_text(angle = 0, vjust = 2), 
          legend.title = element_text(),
          legend.box.just = "center",
          legend.position = "right"
        )
    },
    aspect_ratio = 1,
    title = "Floods and earthquakes are the most damaging natural disasters in Pakistan.",
    subtitle = "Decadal average: Number of deaths and economic damages (% GDP) from natural disasters",
    note = "Note: Decadal figures are measured as the annual average over the subsequent ten-year period.",
    source = "Source: Our World in Data."
  )
}

fig_ch1_natural_disasters()

figure_save_draft_png(fig_ch1_natural_disasters(), style_atlas, "../drafts/fig_ch1_natural_disasters.png", height=4.1, width=5.5)
```


```{r, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=6.5, out.width=800, dpi=200}
fig_ch1_projected_annual_mean_temperature <- function() {
  
  # data
  df <- read_csv("../data/projected-mean-temperature.csv")
  color_list <- c("#303036", "#7FB7BE", "#D3F3EE", "#DACC3E", "#BC2C1A", "#7D1538")

  # chart
  figure(
    data = df,
    plot = function(df, style = style_atlas()) {
      ggplot(df, aes(x=Year, y=Mean, color=Projection)) +
      geom_line(aes(x=Year, y=Mean, color=Projection), size=2) +
      geom_ribbon(aes(ymin=`10-90th Percentile Range (low)`, ymax=`10-90th Percentile Range (high)`, 
                      fill=Projection),color="grey70",alpha=0.2) +
      scale_x_continuous(breaks = bracketed_breaks(df$Year), expand=c(0,0)) +
      scale_y_continuous(
        position="left",
        sec.axis = dup_axis(
          breaks = df %>% filter(Year == max(Year)) %>% pull(Mean) %>% repel(gap=6),
          labels = df %>% filter(Year == max(Year)) %>% pull(Projection)
        )) +
      annotate("text", x = 2005, y = 22.3, label = "Hist. Ref. Per.\n1995-2014", size = 3, family = style$family, color=style$colors$text) +
      scale_fill_manual(values=color_list) + scale_color_manual(values=color_list) +
      geom_vline(xintercept = 2014, linetype = "dashed") +
      style$theme()
    },
    aspect_ratio = 1,
    title = "Pakistan faces rates of warming considerably above the global average.",
    subtitle = "Projected Annual Mean Temperature between 2015-2100 (°C) in Pakistan (Baseline: 1995-2014, Multi-Model Ensemble)",
    source = "Source: World Bank (2022). https://climateknowledgeportal.worldbank.org/country/pakistan/climate-data-projections."
  )
}

fig_ch1_projected_annual_mean_temperature()

figure_save_draft_png(fig_ch1_projected_annual_mean_temperature(), style_atlas, "../drafts/fig_ch1_projected_annual_mean_temperature.png", height=4.1, width=6.5)
```




## 1.3	National GHG Emission Profile 

```{r, message=FALSE, warning = FALSE, fig.height=5.1, fig.width=5.5, out.width=800, dpi=200}
fig_ch1_greenhouse_gas_emissions <- function() {
  
  # data
  df <- read_csv("../data/historical_emissions.csv")
  df <- df[-c(1,2),] %>%
    gather(key="Year", value="Emissions", "2018":"1990") %>%
    select(Sector, Year, Emissions) %>%
    mutate(Year = as.numeric(Year))
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_atlas()) {
      ggplot(df, aes(x = Year, y = Emissions, group = Sector, color = Sector)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$Year), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df %>% filter(Year == max(Year)) %>% pull(Emissions) %>% repel(gap=6),
            labels = df %>% filter(Year == max(Year)) %>% pull(Sector)
          )) +
        scale_color_manual(values = c(
          "Agriculture" = "#A43031", 
          "Building" = "#888D8E",   
          "Bunker Fuels" = "#888D8E",   
          "Electricity/Heat" = "#CB6655",   
          "Energy" = "#A41623",   
          "Fugitive Emissions" = "#888D8E",  
          "Industrial Processes" = "#888D8E",
          "Land-Use Change and Forestry" = "#888D8E",
          "Manufacturing/Construction" = "#F19C79",
          "Other Fuel Combustion" = "#888D8E",
          "Transportation" = "#DE8167",
          "Waste" = "#888D8E"),
          labels = unique(df$Sector)) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Energy and agriculture sectors take up the largest portions of greenhouse gas emissions in Pakistan.",
    subtitle = "Historical Country Greenhouse Gas Emissions (MtCO2e), 1990-2018",
    source = "Source: Climate Watch Historical Country Greenhouse Gas Emissions Data (1990-2018)."
  )
}

fig_ch1_greenhouse_gas_emissions()

figure_save_draft_png(fig_ch1_greenhouse_gas_emissions(), style_atlas, "../drafts/fig_ch1_greenhouse_gas_emissions.png", height=5.1, width=5.5)
```


## 1.4	Pakistan’s Core Development and Climate Priorities

```{r, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=4.1, out.width=800, dpi=200}
library(ggradar)
library(showtext)

fig_ch1_vulnerability <- function() {
  
  # data
  df <- read_csv("../data/vulnerability.csv")

  # add regions and income levels
  df <- df %>%
    rename(iso3c = ISO3) %>%
    left_join(wbgref$countries$regions, by="iso3c") %>%
    left_join(wbgref$countries$incomegroups, by="iso3c")
  
  # calculate aggregates by regions
  region_aggregates <- df %>%
    group_by(region_iso3c) %>% summarize(ecosystems = mean(ecosystems, na.rm=TRUE),
                                         food = mean(food, na.rm=TRUE),
                                         health = mean(health, na.rm=TRUE),
                                         habitat = mean(habitat, na.rm=TRUE),
                                         infrastructure = mean(infrastructure, na.rm=TRUE),
                                         water = mean(water, na.rm=TRUE)) %>%
    rename(iso3c = region_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$regions$labels), Name = wbgref$regions$labels), by="iso3c")
    
  # calculate aggregates by income levels
  income_level_aggregates <- df %>%
    group_by(income_level_iso3c) %>% summarize(ecosystems = mean(ecosystems, na.rm=TRUE),
                                         food = mean(food, na.rm=TRUE),
                                         health = mean(health, na.rm=TRUE),
                                         habitat = mean(habitat, na.rm=TRUE),
                                         infrastructure = mean(infrastructure, na.rm=TRUE),
                                         water = mean(water, na.rm=TRUE)) %>%
    rename(iso3c = income_level_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$incomes$labels), Name = wbgref$incomes$labels), by="iso3c")
  
  # merge and select
  df <- df %>%
    bind_rows(region_aggregates, income_level_aggregates) %>%
    filter(iso3c == "PAK" | iso3c == "LMC" | iso3c == "SAS") %>%
    select(Name, ecosystems, food, health, habitat, infrastructure, water)
  
  # rescale
  min <- 0.3
  max <- 0.9
  min_max_norm <- function(x) {
    (x - min) / (max - min)
  }
  df <- df %>%
    mutate(ecosystems = min_max_norm(ecosystems)) %>%
    mutate(food = min_max_norm(food)) %>%
    mutate(health = min_max_norm(health)) %>%
    mutate(habitat = min_max_norm(habitat)) %>%
    mutate(infrastructure = min_max_norm(infrastructure)) %>%
    mutate(water = min_max_norm(water))
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_atlas()) {
      ggradar(
        df,
        font.radar = style$family,
        values.radar = c(min, (min+max)/2, max),
        grid.min = 0, grid.mid = 0.5, grid.max = 1,
        grid.label.size = 3,  # Affects the grid annotations (0%, 50%, etc.)
        axis.label.size = 3, # Afftects the names of the variables
        group.point.size = 3   # Simply the size of the point 
      ) +
      style$theme() +
      theme(
        line = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        legend.position = c(1, 0),  
        legend.justification = c(1, 0),
        legend.text = element_text(size = 7, family = style$family),
        legend.key = element_rect(fill = NA, color = NA),
        legend.background = element_blank()
      )
    },
    aspect_ratio = 1,
    title = "Pakistan's vulnerability in six life-supporting sectors.",
    subtitle = "Vulnerability scores (0-1 lower is better), 2019",
    note = "Note: Vulnerability measures a country's exposure, sensitivity and ability to adapt to the negative impact of climate change.",
    source = "Source: The Notre Dame-Global Adaptation Index (ND-GAIN) Country Index."
  )
}

fig_ch1_vulnerability()

figure_save_draft_png(fig_ch1_vulnerability(), style_atlas, "../drafts/fig_ch1_vulnerability.png", height=4.1, width=4.1)
```




```{r, message=FALSE, warning = FALSE, fig.height=4.1, fig.width=4.1, out.width=800, dpi=200}
library(ggradar)
library(showtext)

fig_ch1_readiness <- function() {
  
  # data
  df <- read_csv("../data/readiness.csv")

  # add regions and income levels
  df <- df %>%
    rename(iso3c = ISO3) %>%
    left_join(wbgref$countries$regions, by="iso3c") %>%
    left_join(wbgref$countries$incomegroups, by="iso3c")
  
  # calculate aggregates by regions
  region_aggregates <- df %>%
    group_by(region_iso3c) %>% summarize(economic = mean(economic, na.rm=TRUE),
                                         governance = mean(governance, na.rm=TRUE),
                                         social = mean(social, na.rm=TRUE)) %>%
    rename(iso3c = region_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$regions$labels), Name = wbgref$regions$labels), by="iso3c")
    
  # calculate aggregates by income levels
  income_level_aggregates <- df %>%
    group_by(income_level_iso3c) %>% summarize(economic = mean(economic, na.rm=TRUE),
                                         governance = mean(governance, na.rm=TRUE),
                                         social = mean(social, na.rm=TRUE)) %>%
    rename(iso3c = income_level_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$incomes$labels), Name = wbgref$incomes$labels), by="iso3c")
  
  # merge and select
  df <- df %>%
    bind_rows(region_aggregates, income_level_aggregates) %>%
    filter(iso3c == "PAK" | iso3c == "LMC" | iso3c == "SAS") %>%
    select(Name, economic, governance, social)
  
  # rescale
  min <- 0.25
  max <- 0.45
  min_max_norm <- function(x) {
    (x - min) / (max - min)
  }
  df <- df %>%
    mutate(economic = min_max_norm(economic)) %>%
    mutate(governance = min_max_norm(governance)) %>%
    mutate(social = min_max_norm(social))
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_atlas()) {
      ggradar(
        df,
        font.radar = style$family,
        values.radar = c(min, (min+max)/2, max),
        grid.min = 0, grid.mid = 0.5, grid.max = 1,
        grid.label.size = 3,  # Affects the grid annotations (0%, 50%, etc.)
        axis.label.size = 3, # Afftects the names of the variables
        group.point.size = 3   # Simply the size of the point 
      ) +
      style$theme() +
      theme(
        line = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        legend.position = c(1, 0),  
        legend.justification = c(1, 0),
        legend.text = element_text(size = 7, family = style$family),
        legend.key = element_rect(fill = NA, color = NA),
        legend.background = element_blank()
      )
    },
    aspect_ratio = 1,
    title = "Pakistan's readiness in economic opportunity, governance, and social structures.",
    subtitle = "Readiness scores (0-1 higher is better), 2019",
    note = "Note: Readiness measures a country’s ability to leverage investments and convert them to adaptation actions.",
    source = "Source: The Notre Dame-Global Adaptation Index (ND-GAIN) Country Index."
  )
}

fig_ch1_readiness()

figure_save_draft_png(fig_ch1_readiness(), style_atlas, "../drafts/fig_ch1_readiness.png", height=4.1, width=4.1)

```


```{r, message=FALSE, warning = FALSE, fig.height=3.1, fig.width=5.5, out.width=800, dpi=200}

fig_ch1_nd_gain <- function() {
  
  # data
  df <- read_csv("../data/ND-gain.csv")

  # add regions and income levels
  df <- df %>%
    rename(iso3c = ISO3) %>%
    left_join(wbgref$countries$regions, by="iso3c") %>%
    left_join(wbgref$countries$incomegroups, by="iso3c")

  # calculate aggregates by regions
  region_aggregates <- df %>%
    group_by(region_iso3c) %>% summarise(across(where(is.double), ~ mean(.x, na.rm = TRUE))) %>%
    rename(iso3c = region_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$regions$labels), Name = wbgref$regions$labels), by="iso3c")
  
  # calculate aggregates by income levels
  income_level_aggregates <- df %>%
    group_by(income_level_iso3c) %>% summarise(across(where(is.double), ~ mean(.x, na.rm = TRUE))) %>%
    rename(iso3c = income_level_iso3c) %>% 
    left_join(data.frame(iso3c = names(wbgref$incomes$labels), Name = wbgref$incomes$labels), by="iso3c")
  
  # merge and select
  df <- df %>%
    bind_rows(region_aggregates, income_level_aggregates) %>%
    filter(iso3c == "PAK" | iso3c == "LMC" | iso3c == "SAS") %>%
    select(-c(region_iso3c, income_level_iso3c)) %>%
    gather(key="Year", value="Gain", "1995":"2019") %>%
    select(iso3c, Name, Year, Gain) %>%
    mutate(Year = as.numeric(Year))
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_atlas()) {
      ggplot(df, aes(x = Year, y = Gain, group = rev(iso3c), color = iso3c)) +
        geom_line(size = style$linesize) +
        scale_x_continuous(breaks = bracketed_breaks(df$Year), expand=c(0,0)) +
        scale_y_continuous(
          position="left",
          sec.axis = dup_axis(
            breaks = df %>% filter(Year == max(Year)) %>% pull(Gain) %>% repel(gap=6),
            labels = df %>% filter(Year == max(Year)) %>% pull(Name)
          )) +
        scale_color_manual(values = c(
          "LMC" = "#888D8E", 
          "SAS" = "#7F7B7A",
          "PAK" = "#8C271E")) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "Pakistan's ND-GAIN dropped by nearly 10% points in 2014.",
    subtitle = "ND-GAIN Country Index (0-100 higher is better), 1995-2019",
    note = "Note: The ND-GAIN Country Index summarizes a country's vulnerability to climate change and other global challenges in combination with its readiness to improve resilience.",
    source = "Source: The Notre Dame-Global Adaptation Index (ND-GAIN) Country Index."
  )
}

fig_ch1_nd_gain()

figure_save_draft_png(fig_ch1_nd_gain(), style_atlas, "../drafts/fig_ch1_nd_gain.png", height=3.1, width=5.5)
```

## 1.5	Aligning Climate Actions with Development Needs 