---
title: "Pakistan CCDR - 03. Country Climate Commitments and Opportunities for Upscaling Climate Action"
date: "03/11/2022"
output:
  github_document: default
  html_document: default
knit: (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_format = "github_document");
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_format = "html_document",
                        output_dir=file.path(dirname(inputFile), "../html/"))                  
      })
---

This chapter will assess the level of ambition and progress to date of existing country climate commitments and policies for building resilience and accelerating decarbonization, including Pakistan’s revised NDCs and assess the extent to which the full implementation of promised NDCs could be constrained by the policy or institutional framework. It will also look at existing private sector engagement in adaptation and mitigation activities and assess options for scaling up private sector participation through policy and institutional reform, as well as the greening of domestic financial institutions. It will provide an overview of green finance markets and instruments and identify policy priorities for their development, with a focus on de-risking, risk transfer, and credit enhancement instruments for climate investment in strategic sectors (urban infrastructure, green transport, renewable energy, agriculture, circular economy). The analysis will be informed by ongoing analytical work under the CEM and IFC investment and advisory on greening of the banking sector and green bonds market, and on-going financial sector work. The expected spending needs along with financing capacities from various sources including the government, private sector and the international development community will be assessed. The analysis will include an evaluation of the potential challenges posed by Pakistan’s federal structure, which has delegated responsibility for most sectoral actions to provinces. It will also examine the ways in which climate actions could be impeded by the institutional design of government departments at the national and provincial levels, or by policies that sustain the underpricing of natural or common pool resources and energy. 


```{r, echo=FALSE, results='hide', message=FALSE}
source("../../styles/SAR_CCDR_style.R")
source("../../utils/CCDR_utils.R")
library(knitr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(treemapify)
library(ggalt)
library(forcats)
library(png)
library(ggpubr)
library(ggrepel)
library(scales)
library(hrbrthemes)
library(viridis)
library(wbstats)
library(wbgcharts)
library(wbgmaps)
library(wbggeo)
library(readr)
library(readxl)
library(gtable)
library(grid)
library(lubridate)
library(extrafont)
# this only needs to be done once
# library(remotes)
# remotes::install_version("Rttf2pt1", version = "1.3.8")
# font_import() 
# loadfonts(device = 'win')
create_wbgref()
```






&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Actors of climate finance

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=2.7, fig.width=6.5, out.width=800, dpi=200}

fig_ch3_actors_of_climate_finance <- function() {
  # data
  df <- read_csv("../data/Actors of Climate Finance.csv")
  df_group <- df %>% group_by(group) %>% summarize(group_sum = sum(value)) %>% 
    mutate(percentage = 100*group_sum/sum(group_sum))
  df <- df %>% 
    mutate(sector.label = paste(sector, value, sep =" ")) %>%
    left_join(df_group, by="group") %>% 
    mutate(group.label = paste(group, " (", round(percentage, 1), "%)" , sep = "" )) %>%   
    select(group.label, sector.label, value)
  
  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
        ggplot(df, aes(area = value, fill = group.label, label = sector.label, subgroup = group.label, subgroup2 = sector.label)) +
        geom_treemap() +
        geom_treemap_subgroup_border(colour = "white", size = 7) +
        geom_treemap_subgroup2_border(colour = "white", size = 3) +
        geom_treemap_subgroup_text(place = "centre", grow = FALSE,
                                   family = style$family, fontface = "bold.italic",
                                   alpha = 0.75, colour = "white", size = 15) +
        geom_treemap_text(family = style$family, colour = "#282D2E", place = "bottomleft",
                          size = 11, grow = FALSE) +
        style$theme()
    },
    aspect_ratio = 1,
    title = "The share of public sector finance was close to that from the private sector actors in Pakistan.",
    subtitle = "Public and Private Actors of Climate Finance in Pakistan (million US$), 2019",
    source = "Source: Climate Policy Initiative."
  )
}

fig_ch3_actors_of_climate_finance()

figure_save_draft_png(fig_ch3_actors_of_climate_finance(), style_SAR_CCDR, "../png/fig_ch3_actors_of_climate_finance.png", height=2.7, width=6.5)
```





&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;

## Climate finance by sector

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=2.7, fig.width=6.5, out.width=800, dpi=200}

fig_ch3_climate_finance_by_sector <- function() {
  
  # data
  df <- read_csv("../data/Climate Finance Sectors.csv")
  df <- df %>%
    mutate(share = round(100*value/sum(value, na.rm = TRUE), 1))

  # chart
  figure(
    data = df,
    plot = function(df, style = style_SAR_CCDR()) {
      df$sector <- as.factor(df$sector)
      df <- df %>% drop_na() %>% mutate(sector=fct_reorder(sector,value))

      ggplot(df, aes(sector, value, label = prettyNum(value,big.mark=","))) +
        geom_segment(aes(y = 0, yend = value, x = sector, xend = sector),
                     color=style$colors$reference,
                     size=style$linesize_reference) +
        geom_point(color=style$colors$spot.primary,
                   size = style$point_size, 
                   stroke = style$point_stroke, 
                   shape = style$shapes$point) +
        #scale_x_discrete(expand=c(0,0.5),labels = sector) +
        scale_y_continuous(expand=c(0,0),limits = c(0, 1800)) +
        geom_text(nudge_x = 0, nudge_y = 60, family = style$family, color=style$colors$text, size = 2.5) +
        coord_flip() +
        style$theme() +
        style$theme_barchart() 
    },
  aspect_ratio = 1,
  title = "The main recipient of the investments was the energy sector.",
  subtitle = "Climate Finance in Pakistan by Sector (million US$), 2019",
  source = "Source: Climate Policy Initiative."
  )
}

fig_ch3_climate_finance_by_sector()

figure_save_draft_png(fig_ch3_climate_finance_by_sector(), style_SAR_CCDR, "../png/fig_ch3_climate_finance_by_sector.png", height=2.7, width=6.5)

```



## Strengthening Policy and Institutional Frameworks to Enable Climate Action 




